---
title: "Underlying model structure comparison - chapter 3"
output: html_notebook
---

Aim: which underlying distribution to use; Poisson, Neg bio or ZIP. 
- 1st comparison: Compare 3 distrubutions
- 2nd comparison: Add  count effect to the poisson - is this then better or the same as neg bio?
- kfold and PPC checks on all
- Produce plots
- Use high var group effects - as justified in "high_var_groupeffects.Rmd"

References:
https://avehtari.github.io/modelselection/CV-FAQ.html#1_Where_to_start
https://statmodeling.stat.columbia.edu/2018/08/03/loo-cross-validation-approaches-valid/
https://avehtari.github.io/modelselection/rats_kcv.html


### Packages, functions and paths
```{r}
library(tidyverse)
library(brms)
library(gridExtra)
library(tidybayes)
library(loo)

source("C:/local_files/phd_scripts/oh_star/thesis_themes.R")
source("C:/local_files/phd_scripts/oh_star/modelling_uncertainty/posterior_predictive_checks/PPC/analysing_brms_models_functions.R")

# notebook specific functions
source('C:/local_files/phd_scripts/oh_star/chap3/underlying_model_structure_FUNCTIONS.R')

data_path <- "C:/Users/lv13916/OneDrive - University of Bristol/Documents/PhD/projects/oh_star/data/rds_rda/modelling_uncertainty/data_with_locations/"
model_save_path <- "C:/Users/lv13916/OneDrive - University of Bristol/Documents/PhD/projects/oh_star/data/rds_rda/modelling_uncertainty/model_comparisons/"
figure_save_path <- "C:/Users/lv13916/OneDrive - University of Bristol/Documents/PhD/writing/chapter3/figures/"
```


### Making zero-balanced subsets of 3 representative AMs
```{r}
all_data <- readRDS(paste0(data_path, "/brms_format_OHSTAR_locations.Rds")) %>%
  filter(!is.na(count) & environment != "individual")

prop_zeros <- dim(all_data %>%
  filter(plate != "plain" & count == 0))[1]/ dim(all_data)[1]
prop_zeros


set.seed(42)

tetra_data <- balanced_random_sample(all_data, "tetra", 0.63, 100) %>%
  select(assay, plate, am, count) %>%
  mutate(log_dilution = ifelse(am == 0, log(0.1), log(1))) %>%
  mutate(assay = as.factor(paste0(assay, "_tetra"))) %>%
  droplevels()

cipro_data <- balanced_random_sample(all_data, "cipro", 0.06, 100) %>%
  select(assay, plate, am, count) %>%
  mutate(log_dilution = ifelse(am == 0, log(0.1), log(1)))%>%
  mutate(assay = as.factor(paste0(assay, "_cipro"))) %>%
  droplevels()

strep_data <- balanced_random_sample(all_data, "strep", 0.32, 100) %>%
  select(assay, plate, am, count) %>%
  mutate(log_dilution = ifelse(am == 0, log(0.1), log(1)))%>%
  mutate(assay = as.factor(paste0(assay, "_strep"))) %>%
  droplevels()

ceph_data <- balanced_random_sample(all_data, "ceph", 0.28, 100) %>%
  select(assay, plate, am, count) %>%
  mutate(log_dilution = ifelse(am == 0, log(0.1), log(1)))%>%
  mutate(assay = as.factor(paste0(assay, "_ceph"))) %>%
  droplevels()

amox_data <- balanced_random_sample(all_data, "amox", 0.60, 100) %>%
  select(assay, plate, am, count) %>%
  mutate(log_dilution = ifelse(am == 0, log(0.1), log(1)))%>%
  mutate(assay = as.factor(paste0(assay, "_amox"))) %>%
  droplevels()

saveRDS(tetra_data, paste0(data_path, "balanced_tetra_100.Rds"))
saveRDS(strep_data, paste0(data_path, "balanced_strep_100.Rds"))
saveRDS(cipro_data, paste0(data_path, "balanced_cipro_100.Rds"))
saveRDS(ceph_data, paste0(data_path, "balanced_ceph_100.Rds"))
saveRDS(amox_data, paste0(data_path, "balanced_amox_100.Rds"))

all_AMs_data <- rbind(tetra_data, strep_data, cipro_data, ceph_data, amox_data)

saveRDS(all_AMs_data, paste0(data_path, "balanced_all_AMs_data.Rds"))

```
## add row number to data - id for each count
```{r}
all_AMs_data
all_AMs_data_countid <-  all_AMs_data %>%
  mutate(count_id = as.factor(paste0("count_", as.character(seq(1,dim(all_AMs_data)[1])))))
```

### Custom priors
- High var to make group effects behave as fixed


```{r}
custom_priors_widergroupSD <- c(
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'),
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'interaction')#, # fix variance high using normal dist
  #set_prior('normal(10, 1)', class = 'sd', nlpar = 'main'), # fix variance high using normal dist
  #set_prior("normal(10, 1)", class = "sd", group = "assay", coef = "Intercept"),
  #set_prior("normal(10, 1)", class = "sd", group = "assay")
)

# no intercepts, so b not needed, no assay effect in main, so main sd not needed
get_prior(bf(
    count ~ main + am * log_inv_logit(interaction), 
    main ~ offset(log_dilution) + (1|assay),
    interaction ~ (1|assay),
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"))

get_prior(bf(
    count ~ offset(log_dilution) + am * log_inv_logit(interaction), 
    interaction ~ (1|assay)-1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"))

custom_priors_widergroupSD


```


# First comparison - what distrubution is the best?
- Use kfold and PPC
- Remember to run kfold straight after running model
- Use dataset with all AMs in
- High number of folds

### Poisson
```{r}
get_prior(bf(
    count ~ main + am * log_inv_logit(interaction), 
    main ~ offset(log_dilution) + (1|assay),
    interaction ~ (1|assay) -1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"))

custom_priors_widergroupSD <- c(
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'),
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'interaction'), # fix variance high using normal dist
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'main')#, # fix variance high using normal dist
  #set_prior("normal(10, 1)", class = "sd", group = "assay", coef = "Intercept"),
  #set_prior("normal(10, 1)", class = "sd", group = "assay")
)

poisson_allAMs_EDIT <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction), 
    main ~ offset(log_dilution) + (1|assay),
    interaction ~ (1|assay) -1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"), 
  prior = custom_priors_widergroupSD,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

poisson_allAMs_EDIT

poisson_allAMs_EDIT <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction), 
    main ~ offset(log_dilution) + (1|assay) -1,
    interaction ~ (1|assay) -1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"), 
  prior = custom_priors_widergroupSD,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

poisson_allAMs_EDIT
saveRDS(poisson_allAMs_EDIT, paste0(model_save_path, "poisson_allAMs_EDIT_widergroupSD.Rds"))

saveRDS(poisson_allAMs, paste0(model_save_path, "poisson_allAMs_widergroupSD.Rds"))
```

```{r}
cv10sfolds <- kfold_split_stratified(K=20, x = poisson_allAMs$data$assay)

kfold_poisson_allAMs <- loo::kfold(poisson_allAMs, K=20, folds = cv10sfolds, save_fits = TRUE, cores = 4)

saveRDS(kfold_poisson_allAMs, paste0(model_save_path, "kfold_poisson_allAMs.Rds"))
```


### Neg bio
```{r}
negbio_allAMs <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction), 
    main ~ offset(log_dilution),
    interaction ~ (1|assay) -1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = negbinomial(link = "log"), 
  prior = custom_priors_widergroupSD,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

negbio_allAMs

saveRDS(negbio_allAMs, paste0(model_save_path, "negbio_allAMs_widergroupSD.Rds"))

cv10sfolds <- kfold_split_stratified(K=20, x = negbio_allAMs$data$assay)

kfold_negbio_allAMs <- loo::kfold(negbio_allAMs, K=20, folds = cv10sfolds, save_fits = TRUE, cores = 4)

saveRDS(kfold_negbio_allAMs, paste0(model_save_path, "kfold_negbio_allAMs.Rds"))

```


### ZIP
```{r}
zip_allAMs <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction), 
    main ~ offset(log_dilution),
    interaction ~ (1|assay) -1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = zero_inflated_poisson(link = "log"), 
  prior = custom_priors_widergroupSD,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

zip_allAMs

saveRDS(zip_allAMs, paste0(model_save_path, "zip_allAMs_widergroupSD.Rds"))

cv10sfolds <- kfold_split_stratified(K=20, x = zip_allAMs$data$assay)

kfold_zip_allAMs <- loo::kfold(zip_allAMs, K=20, folds = cv10sfolds, save_fits = TRUE, cores = 4)

saveRDS(kfold_zip_allAMs, paste0(model_save_path, "kfold_zip_allAMs.Rds"))

```


### Plotting strep comparisons between poisson, neg bio, zip
```{r}
# picking 50 assays randomly to plot:
rand_sample <- sample(levels(poisson_allAMs$data$assay), 50, replace = FALSE) #for plotting

#zip_allAMs
#negbio_allAMs
#poisson_allAMs

# Poisson
plot_poisson <- ppcheck_ordered_with_raw_count(model = poisson_allAMs,
                                           data = poisson_allAMs$data,
                                           subset = rand_sample,
                                           title = "Poisson model")
plot_poisson 

ggsave(paste0(figure_save_path, "poisson_allAMs_ppcheck.jpg"), height = 6, width = 8)

# Negbio
plot_negbio <- ppcheck_ordered_with_raw_count(model = negbio_allAMs,
                                           data = negbio_allAMs$data,
                                           subset = rand_sample,
                                           title = "Negative binomial model")
plot_negbio
ggsave(paste0(figure_save_path, "negbio_allAMs_ppcheck.jpg"), height = 6, width = 8)

# ZIP
plot_zip <- ppcheck_ordered_with_raw_count(model = zip_allAMs,
                                           data = zip_allAMs$data,
                                           subset = rand_sample,
                                           title = "Zero-inflated Poisson model")
plot_zip
ggsave(paste0(figure_save_path, "zip_allAMs_ppcheck.jpg"), height = 6, width = 8)


```


## Plotting custom model parameters - r and zi
- Note - in thesis shape parameter is called r, but called k in brms

### Neg bio shape parameter
```{r, fig.width = 8, fig.height = 6}

poisson_allAMs <- readRDS(paste0(model_save_path, "poisson_allAMs_widergroupSD.Rds"))
negbio_allAMs <- readRDS(paste0(model_save_path, "negbio_allAMs_widergroupSD.Rds"))


round(mean((negbio_allAMs %>%
  spread_draws(shape))$shape),1)
round(quantile((negbio_allAMs %>%
  spread_draws(shape))$shape, 0.025), 1)
round(quantile((negbio_allAMs %>%
  spread_draws(shape))$shape, 0.975), 1)

mu <- mean(negbio_allAMs$data$count)

r <- mean((negbio_allAMs %>%
  spread_draws(shape))$shape)


ggplot() +
  geom_histogram(aes(x = rnbinom(100000, s=r, m= mu)), binwidth = 1, alpha = 0.5, fill = dual_blues[1]) +
    geom_histogram(aes(x = rpois(100000, lambda= mu)), binwidth = 1, alpha = 0.5, fill = dual_blues[2]) +
  ggtitle(paste("r =", as.character(round(r, 2))))+
  xlab("Colony count")+
  ylab("Count")+
  ylim(0, 6000) +
  xlim(0,150) +
  theme_thesis() +
  theme(axis.ticks.y = element_blank(),
        axis.text.y = element_blank())

#ggsave(paste0(figure_save_path, "negbio_versus_poisson_compare_allAMs.jpg"), height = 6, width = 8)

negbio_allAMs %>%
  spread_draws(shape) %>%
  ggplot() +
  geom_histogram(aes(x = shape), fill = dual_blues[1])+
  theme_thesis() +
  ylab("Count")+
  xlab("Shape parameter (r)")

#ggsave(paste0(figure_save_path, "negbio_allAMs_shape_para.jpg"), height = 6, width = 8)


mu
r
```

### ZIP zi parameter
```{r}
round(mean((zip_allAMs %>%
  spread_draws(zi))$zi), 3)
round(quantile((zip_allAMs %>%
  spread_draws(zi))$zi, 0.025), 3)
round(quantile((zip_allAMs %>%
  spread_draws(zi))$zi, 0.975), 3)


zip_allAMs %>%
  spread_draws(zi) %>%
  ggplot() +
  geom_histogram(aes(x = zi), fill = dual_blues[2])+
  theme_thesis() +
  ylab("Count")+
  xlab("Zero inflation parameter (zi)")

ggsave(paste0(figure_save_path, "zip_allAMs_zi_para.jpg"), height = 6, width = 8)
```




## kfold comparisons
```{r}
loo_compare(kfold_poisson_allAMs, kfold_negbio_allAMs, kfold_zip_allAMs)

kfold_poisson_allAMs
kfold_negbio_allAMs
kfold_zip_allAMs

```



# Second comparison - Possion with count effect versus negbio
- Use streptomycin data
- Run an edited possion model with a high var count effect

```{r}
custom_priors_widergroupSD_overdis <- c(
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'),
  #set_prior('normal(0, 100)', class = 'b', nlpar = 'overdis'),
  set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'interaction'), # fix variance high using normal dist
  set_prior('student_t(3,0,10)', class = 'sd', nlpar = 'overdis')#,
  #set_prior('normal(10, 1)', class = 'sd', nlpar = 'main') # fix variance high using normal dist
)


custom_priors_widergroupSD <- c(
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'),
  set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'interaction')#, # fix variance high using normal dist
  #set_prior('normal(10, 1)', class = 'sd', nlpar = 'main'), # fix variance high using normal dist
  #set_prior("normal(10, 1)", class = "sd", group = "assay", coef = "Intercept"),
  #set_prior("normal(10, 1)", class = "sd", group = "assay")
)

all_AMs_data_countid
```

### Model with overdis as nl parameter
```{r}
poisson_all_AMs_countef <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction) + overdis, 
    overdis ~ (1|count_id) -1,
    main ~ offset(log_dilution),
    interaction ~ (1|assay) -1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"), 
  prior = custom_priors_widergroupSD_overdis,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

saveRDS(poisson_all_AMs_countef, paste0(model_save_path, "poisson_all_AMs_countef.Rds"))
poisson_all_AMs_countef
# run kfold before clearing env
cv10sfolds <- kfold_split_stratified(K=20, x = poisson_all_AMs_countef$data$assay)

kfold_poisson_all_AMs_countef <- loo::kfold(poisson_all_AMs_countef, K=20, folds = cv10sfolds, save_fits = TRUE, cores = 4)

saveRDS(kfold_poisson_all_AMs_countef, paste0(model_save_path, "kfold_poisson_all_AMs_countef.Rds"))
#```
plot_poisson_countef <- ppcheck_ordered_with_raw_count(model = poisson_all_AMs_countef,
                                           data = poisson_all_AMs_countef$data,
                                           subset = rand_sample,
                                           title = "Poisson with added count group effect")+
  ylim(10^-20, 1) 

plot_poisson_countef

ggsave(paste0(figure_save_path, "plot_poisson_countef_ppcheck.jpg"), height = 6, width = 8)

```

```{r}
custom_priors_widergroupSD_overdis_EDIT <- c(
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'),
  #set_prior('normal(0, 100)', class = 'b', nlpar = 'overdis'),
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'interaction'), # fix variance high using normal dist
  set_prior('student_t(3,0,10)', class = 'sd', nlpar = 'overdis'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'main') # fix variance high using normal dist
)

poisson_all_AMs_countef_EDIT <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction) + overdis, 
    overdis ~ (1|count_id) -1,
    main ~ offset(log_dilution) + (1|assay) -1,
    interaction ~ (1|assay) -1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"), 
  prior = custom_priors_widergroupSD_overdis_EDIT,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

```


### Editted model 24/11 - move count effect to first line of equation - don't make new non linear para
```{r}
all_AMs_data_countid


poisson_all_AMs_countef_nooverdis <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction) + (1|count_id), 
    main ~ offset(log_dilution) + (1|assay),
    interaction ~ (1|assay),
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"), 
  prior = custom_priors_widergroupSD,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

saveRDS(poisson_all_AMs_countef_nooverdis, paste0(model_save_path, "poisson_all_AMs_countef_nooverdis.Rds"))

# run kfold before clearing env
cv10sfolds <- kfold_split_stratified(K=20, x = poisson_all_AMs_countef$data$assay)

kfold_poisson_all_AMs_countef <- loo::kfold(poisson_all_AMs_countef, K=20, folds = cv10sfolds, save_fits = TRUE, cores = 4)

saveRDS(kfold_poisson_all_AMs_countef, paste0(model_save_path, "kfold_poisson_all_AMs_countef.Rds"))

plot_poisson_countef <- ppcheck_ordered_with_raw_count(model = poisson_all_AMs_countef,
                                           data = poisson_all_AMs_countef$data,
                                           subset = rand_sample,
                                           title = "Poisson with added count group effect") +
  ylim(10^-30, 1) 

plot_poisson_countef

ggsave(paste0(figure_save_path, "plot_poisson_countef_ppcheck.jpg"), height = 6, width = 8)

```

#```{r}
all_AMs_data_countid

custom_priors_widergroupSD_overdis_normal05 <- c(
  set_prior('normal(0, 5)', class = 'b', nlpar = 'overdis'),
  set_prior('student_t(3,0,10)', class = 'sd', nlpar = 'overdis'),
  set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'interaction'), # fix variance high using normal dist
  set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'main') # fix variance high using normal dist
)

poisson_all_AMs_countef_normal05 <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction) + overdis, 
    overdis ~ (1|count_id),
    main ~ offset(log_dilution) + (1|assay),
    interaction ~ (1|assay),
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"), 
  prior = custom_priors_widergroupSD_overdis_normal05,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

saveRDS(poisson_all_AMs_countef_normal05, paste0(model_save_path, "poisson_all_AMs_countef_nooverdis_normal05.Rds"))
#```
#```{r}
poisson_all_AMs_countef_normal05
#```

#```{r}
poisson_all_AMs_countef <- readRDS(paste0(model_save_path, "poisson_all_AMs_countef.Rds"))

poisson_all_AMs_countef
#```

### Removing global intercepts from model - should just be 1
#```{r}
custom_priors_widergroupSD_overdis

custom_priors_widergroupSD_overdis_nointercept <- c(
  set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'),
  #set_prior('normal(0, 100)', class = 'b', nlpar = 'overdis'),
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'interaction'), # fix variance high using normal dist
  set_prior('student_t(3,0,10)', class = 'sd', nlpar = 'overdis'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'main') # fix variance high using normal dist
)

poisson_all_AMs_countef_no_intercept <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction) + overdis, 
    overdis ~ (1|count_id) -1,
    main ~ offset(log_dilution) + (1|assay) -1,
    interaction ~ (1|assay),
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"), 
  prior = custom_priors_widergroupSD_overdis_nointercept,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

poisson_all_AMs_countef_no_intercept
saveRDS(poisson_all_AMs_countef_no_intercept, paste0(model_save_path, "poisson_all_AMs_countef_no_intercept.Rds"))

# run kfold before clearing env
cv10sfolds <- kfold_split_stratified(K=20, x = poisson_all_AMs_countef_no_intercept$data$assay)

kfold_poisson_all_AMs_countef_no_intercept <- loo::kfold(poisson_all_AMs_countef_no_intercept, K=20, folds = cv10sfolds, save_fits = TRUE, cores = 4)

saveRDS(kfold_poisson_all_AMs_countef_no_intercept, paste0(model_save_path, "kfold_poisson_all_AMs_countef_no_intercept.Rds"))

set.seed(42)
rand_sample <- sample(levels(poisson_all_AMs_countef_no_intercept$data$assay), 50, replace = FALSE) #for plotting

plot_poisson_countef <- ppcheck_ordered_with_raw_count(model = poisson_all_AMs_countef_no_intercept,
                                           data = poisson_all_AMs_countef_no_intercept$data,
                                           subset = rand_sample,
                                           title = "Poisson with added count group effect, no intercept")

plot_poisson_countef

set.seed(42)
rand_sample <- sample(levels(negbio_allAMs$data$assay), 50, replace = FALSE) #for plotting

negbio_allAMs <- readRDS(paste0(model_save_path, "negbio_allAMs_widergroupSD.Rds"))

plot_negbio <- ppcheck_ordered_with_raw_count(model = negbio_allAMs,
                                           data = negbio_allAMs$data,
                                           subset = rand_sample,
                                           title = "Neg bio")

plot_poisson_countef
plot_negbio
kfold_poisson_all_AMs_countef_no_intercept
#```

### Results comparison
```{r}
saveRDS(kfold_poisson_all_AMs_countef_no_intercept, paste0(model_save_path, "kfold_poisson_all_AMs_countef_no_intercept.Rds"))
saveRDS(kfold_negbio_allAMs, paste0(model_save_path, "kfold_negbio_allAMs.Rds"))
saveRDS(kfold_poisson_allAMs, paste0(model_save_path, "kfold_poisson_allAMs.Rds"))


kfold_poisson_allAMs <- readRDS(paste0(model_save_path, "kfold_poisson_allAMs.Rds"))
kfold_negbio_allAMs <- readRDS(paste0(model_save_path, "kfold_negbio_allAMs.Rds"))
kfold_zip_allAMs <- readRDS(paste0(model_save_path, "kfold_zip_allAMs.Rds"))


kfold_poisson_allAMs_countef_no_intercept <- readRDS(paste0(model_save_path, "kfold_poisson_all_AMs_countef_no_intercept.Rds"))
poisson_all_AMs_countef_no_intercept

loo_compare_results <- loo_compare(
                                   kfold_poisson_allAMs_countef_no_intercept,
                                   kfold_zip_allAMs)

loo_compare_results
saveRDS(loo_compare_results, paste0(model_save_path, "loo_compare_results.Rds"))

loo_compare_results <- readRDS(paste0(model_save_path, "loo_compare_results.Rds"))
loo_compare_results
saveRDS(poisson_all_AMs_countef_no_intercept, paste0(model_save_path, "poisson_all_AMs_countef_no_intercept.Rds"))



attr(kfold_poisson_allAMs,"yhash")
poisson_all_AMs_countef_no_intercept
prior_summary(poisson_all_AMs_countef_no_intercept)

negbio_allAMs <- readRDS(paste0(model_save_path, "negbio_allAMs_widergroupSD.Rds"))
poisson_allAMs_widergroupSD <- readRDS(paste0(model_save_path, "poisson_allAMs_widergroupSD.Rds"))

poisson_allAMs_widergroupSD
prior_summary(poisson_allAMs_widergroupSD)
negbio_allAMs

```

### Non-wide priors
```{r}
get_prior(bf(
    count ~ main + am * log_inv_logit(interaction), 
    main ~ offset(log_dilution) + (1|assay),
    interaction ~ (1|assay) -1 ,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"))

custom_priors_normal_SD <- c(
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'),
  set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
  set_prior('student_t(3,0,4.3)', class = 'sd', nlpar = 'interaction'), 
  set_prior('student_t(3,0,4.3)', class = 'sd', nlpar = 'main')#, 
  #set_prior("normal(10, 1)", class = "sd", group = "assay", coef = "Intercept"),
  #set_prior("normal(10, 1)", class = "sd", group = "assay")
)

poisson_allAMs_EDIT_nonwidepriors <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction), 
    main ~ offset(log_dilution) + (1|assay),
    interaction ~ (1|assay) -1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"), 
  prior = custom_priors_normal_SD,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)

poisson_allAMs_EDIT_nonwidepriors

saveRDS(poisson_allAMs_EDIT_nonwidepriors, paste0(model_save_path, "poisson_allAMs_EDIT_nonwidepriors.Rds"))

```

### Removing intercept from main
```{r}
custom_priors_widergroupSD <- c(
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'),
  #set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
  set_prior('normal(10, 1)', class = 'sd', nlpar = 'interaction')#, # fix variance high using normal dist
  #set_prior('normal(10, 1)', class = 'sd', nlpar = 'main'), # fix variance high using normal dist
  #set_prior("normal(10, 1)", class = "sd", group = "assay", coef = "Intercept"),
  #set_prior("normal(10, 1)", class = "sd", group = "assay")
)


poisson_allAMs_EDIT_nointercepts <- brm(
  bf(
    count ~ main + am * log_inv_logit(interaction), 
    main ~ offset(log_dilution) + (1|assay) -1,
    interaction ~ (1|assay) -1,
    nl = T
  ),
  data = as.data.frame(all_AMs_data_countid), 
  family = poisson(link = "log"), 
  prior = custom_priors_widergroupSD,
  iter = 4000, warmup = 2000, chains = 4, cores = 4, 
  backend = "cmdstanr",
  threads = threading(2), #8 cores used
  silent = F,
  save_pars = save_pars(group = TRUE)
)
```


