---
title: "R Notebook"
output: html_notebook
---

Create predictors, tidy and join into a final RF dataset - '/Users/lv13916/Library/CloudStorage/OneDrive-UniversityofBristol/Documents/PhD/projects/synergy/data/synergy_RF.Rds'

### Load libraries and path
```{r}
library(tidyverse)
library(lubridate)

path <- "/Users/lv13916/Library/CloudStorage/OneDrive-UniversityofBristol/Documents/PhD/projects/synergy/data/"
```

```{r}
mg_kg_outcomes_all_tidy_no_outlier <- readRDS(paste0(path, 'mg_kg_outcomes_all_tidy_no_outlier.Rds'))

herd_years_in_df <- mg_kg_outcomes_all_tidy_no_outlier %>%
  select(premises_year, premises_id, interherd_premises_id, region, year)

premises_year_spine <- tibble(premises_year = unique(herd_years_in_df$premises_year))
premises_year_spine # 934


```

### 1) Number of purchases
```{r}
synergy_abs_mgkg_tidy <- readRDS(paste0(path, 'synergy_abs_mgkg_tidy.Rds'))

n_visits_df <- synergy_abs_mgkg_tidy %>%
  select(premises_year, visit_id) %>%
  distinct() %>%
  group_by(premises_year) %>%
  summarise(n_visits = n()) 

n_visits_df %>%
  ggplot() +
  geom_histogram(aes(n_visits))

n_visits_df <- premises_year_spine %>%
  left_join(n_visits_df, by = 'premises_year') %>%
  distinct()
```

### 2) Most commonly used vet
```{r}
synergy_abs_mgkg_tidy <- readRDS(paste0(path, 'synergy_abs_mgkg_tidy.Rds'))
synergy_abs_mgkg_tidy

# from: https://www.tutorialspoint.com/r/r_mean_median_mode.htm
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

synergy_abs_mgkg_tidy %>%
  count(premises_year, vet_id) 
  
vet_used <- synergy_abs_mgkg_tidy %>%
  group_by(premises_year) %>%
  summarise(most_common_vet = getmode(vet_id))

vet_used %>%
  count(premises_year) %>%
  filter(n !=1)

vet_used <- premises_year_spine %>%
  left_join(vet_used, by = 'premises_year') %>%
  distinct()

vet_used
```

### 3) Proportion of herd recieving DCT in previous year
```{r}
synergy_abs_mgkg_tidy <- readRDS(paste0(path, 'synergy_abs_mgkg_tidy.Rds'))

all_premises_years <- tibble('premises_year' = unique(synergy_abs_mgkg_tidy$premises_year))

years_with_DCT <- synergy_abs_mgkg_tidy %>% #1,099
  filter(im_type == 'DCT') %>%
  count(premises_year)

years_with_no_DCT <- all_premises_years %>% # 135
  left_join(years_with_DCT, by = 'premises_year') %>%
  filter(is.na(n)) %>%
  mutate(prop_herd_DCT = 0) %>%
  select(-n)

prop_herd_DCT_current_year <- synergy_abs_mgkg_tidy %>% 
  filter(im_type == 'DCT') %>% # years will no DCT sales won't show
  mutate(tubes_sold = quantity * unit_correction) %>%
  group_by(premises_year, premises_id, year) %>% # rolling_12_month_av is herd size rolling so monthly
  summarise(sum_tubes = sum(tubes_sold, na.rm = T),
            mean_herd_size = mean(rolling_12_month_av)) %>%
  mutate(DCT_doses_sold = sum_tubes/4,
         prop_herd_DCT = DCT_doses_sold/mean_herd_size,
         prop_herd_DCT = ifelse(prop_herd_DCT > 1, 1, prop_herd_DCT),
         match_year = year(year)) %>%
  distinct() %>%
  ungroup() %>%
  select(prop_herd_DCT, premises_year, year, premises_id, match_year)

first_match <- prop_herd_DCT_current_year %>% # all matches lagged by a year
  select(premises_id, year, match_year) %>%
  distinct() %>%
  mutate(year_num = year(year),
         match_year = year_num - 1) %>%
  select(-year) %>%
  left_join(prop_herd_DCT_current_year, by = c('match_year', 'premises_id')) 
  
matched_1 <- first_match %>%
  filter(!is.na(prop_herd_DCT))

matched_2 <- first_match %>% # just those which haven't got a previous year, use current year as a proxy
  filter(is.na(prop_herd_DCT)) %>%
  mutate(match_year = match_year + 1) %>%
  select(-prop_herd_DCT, -premises_year, -year) %>%
  ungroup() %>%
  left_join(prop_herd_DCT_current_year, by = c('match_year', 'premises_id'))

all_matched <- rbind((rbind(matched_1, matched_2) %>% # add on those with no DCT
  select(premises_year, prop_herd_DCT)),
  years_with_no_DCT)

DCT_prop <- all_matched

DCT_prop <- premises_year_spine %>%
  left_join(DCT_prop, by = 'premises_year') %>%
  distinct()

DCT_prop
```

### 4) Calving pattern
- Self reported, from 2018/19 herd health plans
```{r}
reported_calving_pattern_with_addition <- readRDS(paste0(path, "reported_calving_pattern_with_addition.Rds"))
reported_calving_pattern_with_addition %>%
  filter(premises_id == '979')

calving_pattern <- herd_years_in_df %>%
  left_join(reported_calving_pattern_with_addition, by = 'premises_id') %>%
  select(premises_year, calving_pattern) %>%
  distinct() 

calving_pattern
```

### 5) Organic versus conventional
- Conv = 0, organic =  1
```{r}
farm_info <- read.csv(paste0(path, "synergy_ds/farm_info.csv")) %>%
  select(PatientReference, farmType)

organic_info <- farm_info %>%
  mutate(premises_id = as.character(PatientReference), 
         organic = ifelse(farmType == 'Organic', 1, 0)) %>%
  select(premises_id, organic)

organic_info <- herd_years_in_df %>%
  left_join(organic_info, by = 'premises_id') %>%
  select(premises_year, organic) %>%
  distinct() 

organic_info
```

### 6) Herd size
```{r}
synergy_abs_mgkg_tidy <- readRDS(paste0(path, 'synergy_abs_mgkg_tidy.Rds'))

herd_size_info <- synergy_abs_mgkg_tidy %>%
  select(premises_year, rolling_12_month_av) %>% # rolling_12_month_av is monthly rolling average, mean across year get year herd size
  group_by(premises_year) %>%
  summarise(herd_size = mean(rolling_12_month_av))

herd_size_info <- premises_year_spine %>%
  left_join(herd_size_info, by = 'premises_year') %>%
  distinct()

```
### 7) Yield 
```{r}
yeild_info <- readRDS(paste0(path, 'yeild_info_per_year_cow.Rds')) %>%
  mutate(premises_year = paste0(premises_id, '_', as.character(year_num), '-01-01')) %>%
  ungroup() %>%
  select(premises_year, total_prod_per_cow)

yeild_info <- premises_year_spine %>%
  left_join(yeild_info, by = 'premises_year') %>%
  distinct()

median(yeild_info$total_prod_per_cow)
```

### 8) Mean parity
```{r}
all_interherd_info <- readRDS(paste0(path, 'all_interherd_info.Rds'))
parities_path <- paste0(path, 'from_interherd_db/new_pull/')

parities_EAST <- read.csv(paste0(parities_path, 'parities_EAST.csv'), stringsAsFactors = F)%>%
  rename(parity = 'Number') %>%
  mutate(animal_id = paste0(Animal, '_', 'synergy_east')) %>%
  left_join(all_interherd_info, by = 'animal_id')
parities_SOUTH <- read.csv(paste0(parities_path, 'parities_SOUTH.csv'), stringsAsFactors = F)%>%
  rename(parity = 'Number') %>%
  mutate(animal_id = paste0(Animal, '_', 'synergy_south'))%>%
  left_join(all_interherd_info, by = 'animal_id')
parities_NORTH <- read.csv(paste0(parities_path, 'parities_NORTH.csv'), stringsAsFactors = F)%>%
  rename(parity = 'Number') %>%
  mutate(animal_id = paste0(Animal, '_', 'synergy_north'))%>%
  left_join(all_interherd_info, by = 'animal_id')

parity_by_year <- rbind(parities_EAST, parities_SOUTH, parities_NORTH) %>%
  mutate(year = year(Date)) %>%
  select(premises_id, parity, year) %>%
  mutate(premises_year = paste0(premises_id, '_', as.character(year), '-01-01')) %>%
  select(premises_year, parity)

parity_info <- premises_year_spine %>%
  left_join(parity_by_year, by = 'premises_year') %>%
  group_by(premises_year) %>%
  summarise(mu_parity = mean(parity))

parity_info %>%
  ggplot() +
  geom_histogram(aes(x = mu_parity))
```

### 9) SCC
```{r}
all_interherd_info <- readRDS(paste0(path, 'all_interherd_info.Rds'))
all_interherd_info
interherd_db_path <- '/Users/lv13916/Library/CloudStorage/OneDrive-UniversityofBristol/Documents/PhD/projects/synergy/data/from_interherd_db/new_pull/'

milk_rec_east <- read.csv(paste0(interherd_db_path, "milk_recording_EAST.csv"), header = T, na.strings = c("NULL", "NA", "N/A", " "))%>%
  mutate(region = "synergy_east")%>%
  mutate(animal_id = paste0(as.character(Animal), '_', region)) %>%
  select(Date, animal_id, SCC)

milk_rec_north <- read.csv(paste0(interherd_db_path, "milk_recording_NORTH.csv"), header = T, na.strings = c("NULL","NA", "N/A", " "))%>%
  mutate(region = "synergy_north")%>%
  mutate(animal_id = paste0(as.character(Animal), '_', region)) %>%
  select(Date, animal_id, SCC)

milk_rec_south <- read.csv(paste0(interherd_db_path, "milk_recording_SOUTH.csv"), header = T, na.strings = c("NULL","NA", "N/A", " "))%>%
  mutate(region = "synergy_south")%>%
  mutate(animal_id = paste0(as.character(Animal), '_', region)) %>%
  select(Date, animal_id, SCC)


all_milk <- rbind(milk_rec_east, milk_rec_north, milk_rec_south)

our_data_animal_ids <- all_interherd_info %>%
  select(premises_id, animal_id)

SCC_with_year <- our_data_animal_ids %>%
  left_join(all_milk, by = 'animal_id') %>%
  filter(!is.na(SCC)) %>%
  mutate(year_num = year(as.Date(Date)),
         premises_year = paste0(premises_id, '_', as.character(year_num), '-01-01'))

SCC_info <- premises_year_spine %>%
  left_join(SCC_with_year, by = 'premises_year') %>%
  group_by(premises_year) %>%
  summarise(mu_SCC = mean(SCC))

SCC_info <- SCC_info %>%
  mutate(mu_SCC_ml = mu_SCC*1000) %>%
  select(premises_year, mu_SCC_ml)

SCC_info
```

### 10) Weather vars
```{r}
weather_vars <- read.csv(paste0(path, "weather_vars.csv"), header = T, na.strings = c("NULL","NA", "N/A", " ")) %>%
  filter(!is.na(year)) %>%
  mutate(year_num = as.numeric(year))

weather_df <- herd_years_in_df %>%
  mutate(year_num = year(year)) %>%
  left_join(weather_vars, by = 'year_num') %>%
  select(premises_year, max_summer_temp, min_winter_temp, ann_mean_rain)
```



## Joining all predictor vars
```{r}
all_predictors <- herd_years_in_df %>%
  select(premises_year, premises_id, year, region) %>%
  left_join(weather_df, by = 'premises_year') %>%
  left_join(SCC_info, by = 'premises_year') %>%
  left_join(parity_info, by = 'premises_year') %>%
  left_join(yeild_info, by = 'premises_year') %>%
  left_join(herd_size_info, by = 'premises_year') %>%
  left_join(organic_info, by = 'premises_year') %>%
  left_join(calving_pattern, by = 'premises_year') %>%
  left_join(DCT_prop, by = 'premises_year') %>%
  left_join(vet_used, by = 'premises_year') %>%
  left_join(n_visits_df, by = 'premises_year') 

all_predictors

# continuous predictors
all_continuous_predictors <- all_predictors %>%
  select(max_summer_temp, min_winter_temp, ann_mean_rain, mu_SCC_ml, mu_parity, total_prod_per_cow, herd_size, prop_herd_DCT, n_visits) 

mu_predictors <- all_continuous_predictors %>%
  summarise_all(~mean(., na.rm = T)) %>%
  gather(key = 'predictor', value = 'mean' )

sd_predictors <- all_continuous_predictors %>%
  summarise_all(~sd(., na.rm = T)) %>%
  gather(key = 'predictor', value = 'sd')

scaling_stats_for_predictors <- mu_predictors %>%
  left_join(sd_predictors, by = 'predictor')

saveRDS(scaling_stats_for_predictors, paste0(path, 'scaling_stats_for_predictors.Rds'))

# transform proportion 
all_predictors_T <- all_predictors %>%
  mutate(prop_herd_DCT = ifelse(prop_herd_DCT == 0, 0.001,
                                ifelse(prop_herd_DCT == 1, 0.999,
                                       prop_herd_DCT)),
         prop_herd_DCT_T = brms::logit_scaled(prop_herd_DCT))

# scale continuous
all_predictors_T_S <- all_predictors_T %>%
  mutate(max_summer_temp_S =  scale(max_summer_temp),
         min_winter_temp_S =  scale(min_winter_temp),
         ann_mean_rain_S =  scale(ann_mean_rain),
         mu_SCC_ml_S =  scale(mu_SCC_ml),
         mu_parity_S =  scale(mu_parity),
         total_prod_per_cow_S =  scale(total_prod_per_cow),
         herd_size_S = scale(herd_size),
         n_visits_S = scale(n_visits),
         prop_herd_DCT_T_S = scale(prop_herd_DCT_T))

all_predictors_T_S_F <- all_predictors_T_S %>%
  mutate(premises_year = as.factor(premises_year),
         premises_id = as.factor(premises_id),
         year = as.factor(year(year)),
         region = as.factor(region),
         calving_pattern_F = as.factor(calving_pattern),
         most_common_vet_F = as.factor(most_common_vet),
         organic_F = organic)

levels(all_predictors_T_S_F$calving_pattern_F)

saveRDS(all_predictors_T_S_F, paste0(path, 'all_predictors_T_S_F.Rds'))
```

## Making complete dataset
### Investigating missing
```{r, fig.width = 6, fig.height = 4}
predictors <- readRDS(paste0(path, 'all_predictors_T_S_F.Rds')) 
outcomes <- readRDS(paste0(path, 'mg_kg_outcomes_all_tidy_T_S.Rds'))

final_predictors <-  predictors %>%
  select(premises_year, premises_id, year, region, ends_with('_S'), ends_with('_F'))

final_predictors <- final_predictors %>% # remove one which doesn't have a region
  filter(!is.na(region)) 

library(naniar)

gg_miss_upset(final_predictors)

final_predictors %>% summarise_all(.funs = ~round(100*sum(is.na(.))/length(.),2)) %>%
  gather(key = 'predictor', value = 'percent_missing')

```

### Dealing with missing
```{r}
final_predictors_no_missing <- final_predictors %>%
  mutate(total_prod_per_cow_S = ifelse(is.na(total_prod_per_cow_S),
                                       mean(final_predictors$total_prod_per_cow_S, na.rm = T),
                                       total_prod_per_cow_S),
         mu_SCC_ml_S = ifelse(is.na(mu_SCC_ml_S),
                                       mean(final_predictors$mu_SCC_ml_S, na.rm = T),
                                       mu_SCC_ml_S),
         organic_F = ifelse(is.na(organic_F),
                                       0, # most common is non-organic
                                       organic_F),
         mu_parity_S = ifelse(is.na(mu_parity_S),
                                       mean(final_predictors$mu_parity_S, na.rm = T),
                                       mu_parity_S),
         prop_herd_DCT_T_S = ifelse(is.na(prop_herd_DCT_T_S),
                                       mean(final_predictors$prop_herd_DCT_T_S, na.rm = T),
                                       prop_herd_DCT_T_S)) 

final_predictors_no_missing %>% 
  filter(if_any(everything(), is.na))
```
### Outcomes
```{r}
outcomes %>% summarise_all(.funs = ~sum(is.na(.))) %>%
  gather(key = 'outcome', value = 'percent_missing')
```
- One herd has missing yeild info so will be excluded from total_mg_kg per L analysis

```{r}
outcomes_scaled_only <- outcomes %>%
  select(premises_year, ends_with('T_S'),
         -total_mgkg_T_S, -total_mgkg_per_L_T_S)

names(outcomes_scaled_only) <- c('premises_year',
                              'total_mgkg_esvac_O',
                              'topical_mgkg_O',
                              'im_mgkg_T_O',
                              'systemic_mgkg_O',
                              'total_mgkg_per_L_esvac_O')

outcomes_scaled_only
```
### Joining scaled
```{r}
#scaled
synergy_RF <- outcomes_scaled_only %>%
  left_join(final_predictors_no_missing, by = 'premises_year') %>%
  select(premises_year, premises_id, year, region, everything()) %>% 
  filter(!is.na(region))

saveRDS(synergy_RF, paste0(path, 'synergy_RF.Rds'))

# unscaled
mg_kg_outcomes_all_tidy_no_outlier <- readRDS(paste0(path, 'mg_kg_outcomes_all_tidy_no_outlier.Rds'))

saveRDS(all_predictors_T_S_F, paste0(path, 'all_predictors_T_S_F.Rds'))

synergy_RF_unscaled <- mg_kg_outcomes_all_tidy_no_outlier %>%
  left_join(all_predictors, by = c('premises_year', 'premises_id', 'year', 'region')) %>%
  select(premises_year, premises_id, year, region, everything()) %>% 
  filter(!is.na(region)) %>%
  mutate(year = as.character(as.numeric(year(year))),
         premises_id = as.character(premises_id))

saveRDS(synergy_RF_unscaled, paste0(path, 'synergy_RF_unscaled.Rds'))
```



