---
title: "Joining data sources to calculate AMU"
output: html_notebook
---

Aim:

- Join antibioitc medicines matched using Monge-Elkan score and manually checked
- Get into format so that all of synergy AMU can be easily calculated
- Export as an Rda which has all AMU products per premises ID and interherd db ID
- Check matches are all okay and units also match
- Calculate AMU mg/kg for each product

Cleaning:
- Check herd size, AMU etc is reasonable
- Add unique identifiers for item sales 

### Load libraries and path
```{r}
library(tidyverse)
library(lubridate)

path <- 'C:/Users/lv13916/OneDrive - University of Bristol/Documents/PhD/projects/synergy/data/'
setwd(path)
```

### Loading in raw data
- Note - the sales data have already had sfh_abs_id matched in Excel via VLOOKUP due to strange string matching problem when trying to do the same in R
```{r}
setwd(path)

complete_abs_matches <- read.csv("amu/complete_abs_matches_v2.csv", stringsAsFactors = F, na.strings=c("","NA", " ", "#NA", "#N/A"))
sales_post2017 <- read.csv("amu/sales_post2017_sfh_id.csv", stringsAsFactors = F, na.strings=c("","NA", " ", "#NA", "#N/A"))
sales_pre2017 <- read.csv("amu/sales_pre2017_sfh_id.csv", stringsAsFactors = F, na.strings=c("","NA", " ", "#NA", "#N/A"))
abs_medicines_database <- read.csv("amu/abs_medicines_database_edit.csv", stringsAsFactors = F, na.strings=c("","NA", " ", "#NA", "#N/A"))

setwd(path)
oh_star_med_db <- read.csv("amu/oh_star_medicines_db.csv", stringsAsFactors = F, na.strings=c("","NA", " ", "#NA", "#N/A"))

dim(complete_abs_matches)
dim(sales_post2017)
dim(sales_pre2017)
dim(abs_medicines_database)


```



rows and cols check: 
433   4
183505     14
820507     15
301  17

### Getting sales data and combining 
- Filter out non-abs
```{r}
setwd(path)

sales_pre2017_tidy <- sales_pre2017[c(1:10, 12, 13, 15)] # select cols
sales_post2017_tidy <- sales_post2017[c(2:14)]
head(sales_pre2017_tidy)
head(sales_post2017_tidy)
names(sales_pre2017_tidy) <- names(sales_post2017_tidy)

pre_n <- dim(sales_pre2017_tidy)[1]
post_n <- dim(sales_post2017_tidy)[1]

all_sales <- rbind(sales_pre2017_tidy, sales_post2017_tidy) %>%
  mutate(source = c(rep("old_db", pre_n), rep("new_db", post_n)))

dim(all_sales) # 1004012, 13
head(all_sales)
names(all_sales) <- tolower(names(all_sales))

all_sales <- all_sales %>%
  filter(!is.na(patientreference))

dim(all_sales) # 1003827, 13
all_sales

n_patients <- dim(all_sales %>%
  count(patientreference))[1]
n_patients # patients = herd, 6238


# adding a sale id - one id for every item sold
all_sales_id <- all_sales %>%
  mutate(sale_num = seq(1, dim(all_sales)[1]),
         sale_txt = rep("sale_", dim(all_sales)[1]),
         sale_id = paste0(sale_txt, sale_num)) %>%
  select(-sale_txt, -sale_num) %>%
  select(sale_id, everything())

# adding a vet visit ID
visit_stats <- all_sales_id %>%
  group_by(workdonedate, patientreference) %>%
  summarise(n = n())

mean(visit_stats$n)
median(visit_stats$n)
quantile(visit_stats$n, 0.25)
quantile(visit_stats$n, 0.75)

n_visits <- dim(visit_stats)[1]

visit_stats <- visit_stats %>%
  ungroup() %>%
  mutate(visit_num = seq(1, n_visits),
         visit_txt = rep("visit_", n_visits),
         visit_id = paste0(visit_txt, visit_num)) %>%
  select(workdonedate, patientreference, visit_id)

all_sales_id <- all_sales_id %>%
  left_join(visit_stats, by = c("workdonedate", "patientreference")) %>%
  select(sale_id, visit_id, everything())

write.csv(all_sales_id, "all_sales.csv")

abs_sales <- all_sales_id %>%
  filter(!is.na(sfh_abs_id))

dim(abs_sales)[1]

dim(abs_sales %>%
  count(patientreference))[1]

dim(abs_sales %>%
  count(visit_id))[1]

write.csv(abs_sales, "abs_sales.csv")
```
- In excluding non-abs sales, we have reduced patients to 2528 and visits to 107560
- To assess number of visits and visit frequency, we will need the data on non-abs visits back

### Matching sales to abs 
- Using complete_abs_matches_v2.csv which is the result of the Monge-Elkan algorithim and manual checking.
- Each database medicine has a unqiue abs_id. Each synergy abs has a unique sfh_abs_id

```{r}
setwd(path)

matches <- complete_abs_matches %>%
  select(sfh_abs_id, abs_id, db_match)

names(abs_medicines_database) <- tolower(names(abs_medicines_database))

abs_medicines_database <- abs_medicines_database %>%
  rename("abs_id" = "med_id")


abs_sales_matched <- abs_sales %>%
  left_join(matches, by = "sfh_abs_id") %>%
  left_join(abs_medicines_database, by = "abs_id")
# 326233
abs_medicines_database

abs_sales_matched %>%
  filter(is.na(sfh_abs_id))

dim(abs_sales_matched)[1] # number of AM active drugs sold


write.csv(abs_sales_matched, "abs_sales_matched.csv")
```

### Adding additonal info from OH-STAR db
- main indication 
- dose
```{r}
oh_star_med_db
```

```{r}
oh_star_med_db_select <- oh_star_med_db %>%
  select(Medicine, ActiveSubstances, Average.daily.dose.rate..mg.kg..mg.dose., Unit.of.dose, Use, Main.indication)

names(oh_star_med_db_select) <- c("db_match", "active_sub", "daily_dose_mgkg", "dose_unit", "delivery_method", "indications")

oh_star_med_db_select %>%
  separate(indications, into = c("a", "b", "c", "d", "e"), ",")

summary <- oh_star_med_db_select %>%
  count(indications) %>%
  arrange(-n) %>%
  select(-n)

summary_indications <- summary %>%
  separate(indications, into = c("a", "b", "c", "d", "e"), ",") %>%
  gather(key= "indication") %>%
  select(value) %>%
  filter(!is.na(value)) %>%
  mutate(value = tolower(value)) %>%
  distinct()

summary_indications

setwd(path)
write.csv(summary_indications, "summary_indications_old.csv") # manually categorised

setwd(path)
summary_indications <- read.csv("summary_indications.csv") %>%
  mutate(across(where(is.character), str_trim))

oh_star_med_db_select <- oh_star_med_db_select %>%
  mutate(indications = tolower(indications)) %>%
  separate(indications, into = c("a", "b", "c", "d", "e"), ",") %>%
  mutate(across(where(is.character), str_trim))

summary_indicationsA <- summary_indications %>%
  mutate(a = old_description)

oh_star_med_db_selectEDIT <- oh_star_med_db_select %>%
  left_join(summary_indicationsA, by = "a") %>%
  rename("indication_category_A" = "indication_category") %>%
  select(-old_description, -a)


summary_indicationsB <- summary_indications %>%
  mutate(b = old_description)

oh_star_med_db_selectEDIT <- oh_star_med_db_selectEDIT %>%
  left_join(summary_indicationsB, by = "b") %>%
  rename("indication_category_B" = "indication_category") %>%
  select(-old_description, -b)

summary_indicationsC <- summary_indications %>%
  mutate(c = old_description)

oh_star_med_db_selectEDIT <- oh_star_med_db_selectEDIT %>%
  left_join(summary_indicationsC, by = "c") %>%
  rename("indication_category_C" = "indication_category") %>%
  select(-old_description, -c)


summary_indicationsD <- summary_indications %>%
  mutate(d = old_description)

oh_star_med_db_selectEDIT <- oh_star_med_db_selectEDIT %>%
  left_join(summary_indicationsD, by = "d") %>%
  rename("indication_category_D" = "indication_category") %>%
  select(-old_description, -d)

summary_indicationsE <- summary_indications %>%
  mutate(e = old_description)

oh_star_med_db_selectEDIT <- oh_star_med_db_selectEDIT %>%
  left_join(summary_indicationsE, by = "e") %>%
  rename("indication_category_E" = "indication_category") %>%
  select(-old_description, -e)

oh_star_med_db_selectEDIT <- oh_star_med_db_selectEDIT %>%
  distinct()

oh_star_med_db_selectTIDY <- oh_star_med_db_selectEDIT %>%
  # mastitis
  mutate(ind_mastitis = ifelse((indication_category_A == "mastitis" | indication_category_B == "mastitis" | indication_category_C == "mastitis"|indication_category_D == "mastitis"|indication_category_E == "mastitis"), TRUE, FALSE),
         ind_mastitis = ifelse(is.na(ind_mastitis), FALSE, ind_mastitis)) %>%
  # resp
  mutate(ind_respiratory = ifelse((indication_category_A == "respiratory" | indication_category_B == "respiratory" |   indication_category_C == "respiratory"|indication_category_D == "respiratory"|indication_category_E == "respiratory"), TRUE, FALSE),
         ind_respiratory = ifelse(is.na(ind_respiratory), FALSE, ind_respiratory)) %>%
  # enteric
  mutate(ind_enteric = ifelse((indication_category_A == "enteric" | indication_category_B == "enteric" |   indication_category_C == "enteric"|indication_category_D == "enteric"|indication_category_E == "enteric"), TRUE, FALSE),
         ind_enteric = ifelse(is.na(ind_enteric), FALSE, ind_enteric)) %>%
  # metritis
  mutate(ind_metritis = ifelse((indication_category_A == "metritis" | indication_category_B == "metritis" |   indication_category_C == "metritis"|indication_category_D == "metritis"|indication_category_E == "metritis"), TRUE, FALSE),
         ind_metritis = ifelse(is.na(ind_metritis), FALSE, ind_metritis)) %>%
  # soft tissue
  mutate(ind_soft = ifelse((indication_category_A == "soft tissue" | indication_category_B == "soft tissue" |   indication_category_C == "soft tissue"|indication_category_D == "soft tissue"|indication_category_E == "soft tissue"), TRUE, FALSE),
         ind_soft = ifelse(is.na(ind_soft), FALSE, ind_soft)) %>%
  # foot
  mutate(ind_foot = ifelse((indication_category_A == "foot" | indication_category_B == "foot" |   indication_category_C == "foot"|indication_category_D == "foot"|indication_category_E == "foot"), TRUE, FALSE),
         ind_foot = ifelse(is.na(ind_foot), FALSE, ind_foot)) %>%
  # systemic
  mutate(ind_systemic = ifelse((indication_category_A == "systemic" | indication_category_B == "systemic" |   indication_category_C == "systemic"|indication_category_D == "systemic"|indication_category_E == "systemic"), TRUE, FALSE),
         ind_systemic = ifelse(is.na(ind_systemic), FALSE, ind_systemic)) %>%
  select(-starts_with("indication_category"))


### doing same with delivery method
oh_star_med_db_selectTIDY %>%
  count(delivery_method)

oh_star_med_db_selectTIDY <-oh_star_med_db_selectTIDY %>%
  mutate(delivery_method = as.factor(delivery_method))

levels(oh_star_med_db_selectTIDY$delivery_method) <- c("DC intramammary",
                                                       "Eye",
                                                       "Footbath",
                                                       "Injection",
                                                       "Intrauterine",
                                                       "LC intramammary",
                                                       "Oral",
                                                       "Oral",
                                                       "Oral",
                                                       "Oral",
                                                       "Spray"
                                                       )

oh_star_med_db_selectTIDY %>%
  count(delivery_method)

oh_star_med_db_selectTIDY

setwd(path)
saveRDS(oh_star_med_db_selectTIDY, "additional_meddb_info.Rds")
```

Categories:

mastitis 
respiratory
enteric
metritis
soft tissue
foot
systemic
other


### Tidying and checking units

```{r}
setwd(path)

abs_sales_matched_tidy <- abs_sales_matched

abs_sales_matched_tidy <- abs_sales_matched_tidy[c(1:3,6:28)] 

names(abs_sales_matched_tidy) <- tolower(names(abs_sales_matched_tidy))

abs_sales_matched_tidy <- abs_sales_matched_tidy %>%
  mutate(workdonedate = as.Date(workdonedate, "%d/%m/%Y"))
  
abs_sales_matched_tidy <- abs_sales_matched_tidy %>%
  mutate(unit.of.concentration_copy = unit.of.concentration) %>%
  separate(unit.of.concentration_copy, sep = "/", into = c(NA, "denom_unit")) %>%
  mutate(actual.quantity.unit = trimws(tolower(actual.quantity.unit)),
         unit_match = ifelse(denom_unit == actual.quantity.unit, 1, 0))

abs_sales_matched_tidy %>%
  filter(itemdescriptionclean == "ubro red 20 pack") %>%
  count(actual.quantity, actual.quantity.unit
)

abs_sales_matched_tidy %>%
  filter(sale_id == "sale_813535")

mismatches <- abs_sales_matched_tidy %>%
  filter(unit_match == 0) %>%
  group_by(actual.quantity.unit, denom_unit, abs_id, sfh_abs_id, itemdescriptionclean) %>%
  count(medicine) %>%
  arrange(desc(n))

mismatches

write.csv(mismatches, "denom_mismatches.csv")

```

### Dealing with unit mismatches
- Manually checked mismatched units and added a correction factor to change units - eg. 1 pack of 120 tubes -> tubes = 120
- Where quantities such as pack sizes was ambiguous, the largest pack size was assume to prevent under estimation
- Where suspension products were given in ml only, it was assumed that 1ml suspension = 1g, although this is likely a slight over estimate
- Noticed some units seem to be incorrect - check very high or very small perscription quantities
- Utocl pessaries - unknown concentration and pack size, but not many used

```{r}
setwd(path)

mismatches_correction <- read.csv("amu/denom_mismatches_unit_correction.csv", stringsAsFactors = F, na.strings=c("","NA", " ", "#NA", "#N/A"))

mismatches_correction <- mismatches_correction %>%
  select(-X, -X.1, -n, -itemdescriptionclean, -medicine)

abs_sales_matched_tidy %>%
  count(unit_match)

abs_sales_matched_tidy <- abs_sales_matched_tidy %>%
  left_join(mismatches_correction, by = c("actual.quantity.unit", "denom_unit", "abs_id", "sfh_abs_id")) %>%
  mutate(unit_correction = ifelse(is.na(unit_correction), 1, unit_correction))

length(unique((abs_sales_matched_tidy$sale_id)))


abs_sales_matched_tidy %>%
  filter(sale_id == "sale_813535")

dim(abs_sales_matched_tidy)

abs_sales %>%
  filter(sale_id == "sale_813535")

abs_sales_matched %>%
  filter(sale_id == "sale_813535")


abs_sales %>%
  filter(sale_id == "sale_827328")

abs_sales_matched %>%
  filter(sale_id == "sale_827328")

setwd(path)
saveRDS(abs_sales_matched_tidy, "amu/abs_sales_matched_tidy.Rda")  

```



- Sales all conserved 

### Getting mg sold 
- Assume negative quantities as NA - refunds? But not clear if the product is exchanged etc.
```{r}
setwd(path)

abs_sales_matched_tidy <- readRDS("amu/abs_sales_matched_tidy.Rda")  

abs_sales_matched_tidy %>%
    filter(sale_id == "sale_813535")

dim(abs_sales_matched_tidy)



abs_sales_matched_tidy %>%
  filter(medicine == "Tetra-Delta Intramammary Suspension") %>%
  filter(source == "old_db")


abs_sales_matched_tidy %>%
  filter(medicine == "Tetra-Delta Intramammary Suspension") %>%
  filter(source == "new_db")
  

abs_sales_matched_joined %>%
  filter(source == "old-db")
```
	
```{r}
abs_sales_matched_calc <- abs_sales_matched_tidy %>%
  mutate(actual.quantity = ifelse(actual.quantity < 0, NA, actual.quantity),
        mg_abs = actual.quantity*unit_correction*concentration..mg.or.iu.)

abs_sales_matched_calc %>%
  filter(medicine == "Tetra-Delta Intramammary Suspension") %>%
  filter(source == "old_db")


abs_sales_matched_calc %>%
  filter(medicine == "Tetra-Delta Intramammary Suspension") %>%
  filter(source == "new_db")
abs_sales_matched_calc

abs_sales_matched_calc <- abs_sales_matched_calc[c(1:16,18:26,28,38:40,44)]

abs_sales_calc_tidy <- abs_sales_matched_calc %>%
  rename("med_name" = "medicine",
         "active_sub" = "activesubstances",
         "med_group" = "therapeuticgroup",
         "num_ingred" = "number.of.am.active.ingredients",
         "conc" = "concentration..mg.or.iu.",
         "conc_unit" = "unit.of.concentration",
         #"form" = "pharmaceuticalform",
         "date" = "workdonedate",
         "item_desc" = "itemdescriptionclean",
         "premises_id" = "patientreference",
         "client_id" = "clientrefnumber",
         "vet_id" = "vetid",
         "quantity" = "actual.quantity",
         "quantity_unit" = "actual.quantity.unit",
         "abs_class" = "class") %>%
         #"species" = "targetspecies")
  select(-db_match, -itemdescription, -itemcode, -use)

head(abs_sales_calc_tidy)
dim(abs_sales_calc_tidy)


saveRDS(abs_sales_calc_tidy, "amu/abs_sales_calc_tidy.Rda")  

```


### Getting herd size infomation
```{r}
setwd(path)
east_stays <- read.csv("from_interherd_db/herd_size_per_monthEAST.csv")
north_stays <- read.csv("from_interherd_db/herd_size_per_monthNORTH.csv")
south_stays <- read.csv("from_interherd_db/herd_size_per_monthSOUTH.csv")
east_stays
names(east_stays) <- c("Id", "month", "herd_size")
names(north_stays) <- c("Id", "month", "herd_size")
names(south_stays) <- c("Id", "month", "herd_size")

north_stays <- north_stays %>%
  mutate(Region = "Synergy_North")
east_stays <- east_stays %>%
  mutate(Region = "Synergy_East")
south_stays <- south_stays %>%
  mutate(Region = "Synergy_South")

all_stays <- rbind(north_stays, south_stays, east_stays) %>%
  mutate(month = as.character(month))

premises_id <- read.csv("synergy_ds/interherdid_premisesid_lookup.csv")

all_stays <- premises_id %>%
  inner_join(all_stays, by = c("Region", "Id")) %>%
  mutate(herd_av_kg = herd_size * 425) %>% # using PCU
  rename("premises_id" = "Patient.Ref")

# converting date time to date
all_stays$month <- sapply(strsplit(all_stays$month, " "), `[`, 1, simplify=TRUE)

all_stays <- all_stays %>%
  mutate(month = as.Date(month, "%Y-%m-%d"))

setwd(path)
saveRDS(all_stays, "all_stays.Rds")

```


### Clear vars because there are large datasets
```{r}
rm(list=ls())

path <- 'C:/Users/lv13916/OneDrive - University of Bristol/Documents/PhD/projects/synergy/data/'
setwd(path)
```


### Joining herd weights and antibiotic mgs sold
- Need to get all stays in period from 2009-11-01
```{r}
setwd(path)
all_stays <- readRDS("all_stays.Rds")
abs_sales_calc_tidy <- readRDS("amu/abs_sales_calc_tidy.Rda")  
head(abs_sales_calc_tidy)

all_stays %>%
  ggplot() +
  geom_line(aes(x = month, y = herd_size, group = premises_id))

all_stays %>%
  group_by(premises_id) %>%
  summarise(mu = mean(herd_size)) %>%
  ggplot() +
  geom_histogram(aes(x = mu))
```


#### Filtering out those with not full info - eg no herd size,AM data for less than a year
```{r}
prem_with_herdsize <- (all_stays %>%
  count(premises_id))$premises_id

length(prem_with_herdsize)
#133 premises with herd size info

# keep only premises that have >a years worth of ABS data
premises_keep <- (abs_sales_calc_tidy %>%
  filter(premises_id %in% prem_with_herdsize) %>%
  group_by(premises_id) %>%
  summarise(time = as.numeric(max(date) - min(date))) %>%
  filter(time > 365) %>%
  arrange(desc(time)))$premises_id

#130 premises have >1 year ABS data

abs_sales_keep <- abs_sales_calc_tidy %>%
  filter(premises_id %in% premises_keep) %>%
  mutate(month = floor_date(date), unit = "month",
         month = as.Date(month, "%Y-%m-%d")) %>%
  select(-unit)

abs_sales_keep <- abs_sales_keep %>%
  filter(premises_id %in% prem_with_herdsize)
#356,238 abs sales  

abs_sales_keep %>%
  count(premises_id)

setwd(path)
saveRDS(abs_sales_keep, "amu/abs_sales_keep.Rds")
# 130 remain

# plotting some to check length at practice
ran <- round(runif(30, 1, max = length(unique(abs_sales_keep$premises_id))))

first_30 <- unique(abs_sales_keep$premises_id)[ran]

abs_sales_keep %>%
  filter(premises_id %in% first_30) %>%
  mutate(premises_id = as.factor(as.character(premises_id))) %>%
  ggplot() + 
  geom_point(aes(x = month, y = premises_id, colour = premises_id)) +
  theme(legend.position = "none")

length_at_practice <- abs_sales_keep %>%
  group_by(premises_id) %>%
  summarise(start_date = min(month),
            end_date = max(month)) %>%
  mutate(diff_days = as.numeric(end_date - start_date),
         diff_year = diff_days/365)

length_at_practice %>%
  ggplot() +
  geom_histogram(aes(x = diff_year))

length_at_practice %>%
  filter(diff_year >= 9)

87/130

max(length_at_practice$diff_year)
```

```{r}
all_stays %>%
  filter(premises_id %in% premises_keep) %>%
  ggplot() +
  geom_line(aes(x =month, y = herd_size, group = as.factor(premises_id))) +
  scale_y_continuous(trans = "log10")

```

### Checking for extreme changes which could be errors
```{r}
all_stays_diff <- all_stays %>%
  mutate(diff = as.numeric(0))

for (i in unique(all_stays$premises_id)){
  diffs <- all_stays %>%
    filter(premises_id == i) %>%
    arrange(month) %>%
    mutate(herd_size_lag = lag(herd_size),
           diff = herd_size - herd_size_lag) %>%
    select(premises_id, month, diff)
  
  all_stays_diff <- all_stays_diff %>%
    left_join(diffs, by = c("premises_id", "month")) %>%
    mutate(diff.x = as.numeric(ifelse(is.na(diff.x), 0, diff.x)),
           diff.y = as.numeric(ifelse(is.na(diff.y), 0, diff.y)),
           diff = diff.y + diff.x) %>%
    select(-diff.y, -diff.x)
}

big_change_premises <- all_stays_diff %>%
  mutate(diff_prop = ifelse(diff/herd_size*100 < 0, diff/herd_size*100*-1, diff/herd_size*100)) %>%
  arrange(desc(diff_prop)) %>%
  filter(diff_prop > 90) %>%
  select(premises_id)

big_change_premises
unique(big_change_premises)


all_stays_diff %>%
    filter(premises_id == "6194") %>%
    ggplot() +
    geom_line(aes(x = month, y = herd_size))

all_stays_diff %>%
    filter(premises_id == "979") %>%
    ggplot() +
    geom_line(aes(x = month, y = herd_size))

all_stays_diff %>%
    filter(premises_id == "5996") %>%
    ggplot() +
    geom_line(aes(x = month, y = herd_size))

all_stays_diff %>%
    filter(premises_id == "1017") %>%
    ggplot() +
    geom_line(aes(x = month, y = herd_size))

all_stays_diff %>%
    filter(premises_id == "2024") %>%
    ggplot() +
    geom_line(aes(x = month, y = herd_size))

all_stays_diff %>%
    filter(premises_id == "4535") %>%
    ggplot() +
    geom_line(aes(x = month, y = herd_size))

all_stays_diff %>%
    filter(premises_id == "563") %>%
    ggplot() +
    geom_line(aes(x = month, y = herd_size))

```

### Smoothing extreme changes using rolling average
```{r}
setwd(path)
all_stays <- readRDS("all_stays.Rda") 

all_stays_copy <- all_stays %>%
  select(-herd_av_kg) %>%
 # filter(premises_id == 236) %>%
  arrange(premises_id, month) %>%
  filter(!(premises_id == 2295)) # duplicate premises_id, can't match with sales correctly so remove

all_stays_copy
all_stays_ref <- all_stays %>%
  select(premises_id, month, herd_size) %>%
  rename("month_match" = "month")


for (i in c(-6:6)){
  print(i)
  new_name <- paste0("herd_size_lag", as.character(i))
  
  editted_all_stays_copy <- all_stays_copy %>%
    mutate(month_match = month %m+% months(i)) %>%
    left_join(all_stays_ref, by = c("premises_id", "month_match")) %>%
    rename("herd_size" = "herd_size.x")
  
  n <- dim(editted_all_stays_copy)[2]
  
  names(editted_all_stays_copy) <- c(names(editted_all_stays_copy)[1:n-1], new_name) 
  all_stays_copy <- editted_all_stays_copy %>%
    select(-month_match)
}


all_stays_copy <- all_stays_copy %>%
  mutate(rolling_12_month_av = rowMeans(select(all_stays_copy, starts_with("herd_size_lag")), na.rm = TRUE)) %>%
  select(premises_id, month, herd_size, rolling_12_month_av)

all_stays_copy %>%
  filter(premises_id == 563) %>%
  ggplot() +
  geom_point(aes(x = month, y = rolling_12_month_av), colour = dual_blues[1]) +
  geom_line(aes(x = month, y = rolling_12_month_av), colour = dual_blues[1]) +
  geom_point(aes(x = month, y = herd_size), colour = dual_blues[2]) +
  geom_line(aes(x = month, y = herd_size), colour = dual_blues[2])

all_stays_copy

all_stays <- all_stays_copy %>%
  select(premises_id, month, rolling_12_month_av) %>%
  left_join(all_stays, by = c("premises_id", "month")) %>%
  mutate(herd_av_kg = rolling_12_month_av*425)


setwd(path)
saveRDS(all_stays, "all_stays.Rds") 

```

# Joining antimicrobial info to get mg/kg
```{r}
setwd(path)

all_stays <-readRDS("all_stays.Rds") 
abs_sales_keep <- readRDS("amu/abs_sales_keep.Rds")
abs_sales_keep

synergy_abs_joined <- abs_sales_keep %>%
  mutate(month = floor_date(date, unit = "month")) %>%
  left_join(all_stays, by =c("month", "premises_id")) 

synergy_abs_joined <- synergy_abs_joined %>%
  filter(!is.na(herd_size))

length(unique(synergy_abs_joined$premises_id)) # 129 premises

synergy_abs_mgkg <- synergy_abs_joined %>%
  mutate(mg_abs = quantity*conc*unit_correction,
         abs_mg_kg = mg_abs/(rolling_12_month_av*425)) # herd size times 425kg = mg/kg

prop_missing = dim(synergy_abs_mgkg %>%
  filter(is.na(abs_mg_kg)))[1]/dim(synergy_abs_mgkg)[1]*100

print(paste("Proportion missing mg of abs:", as.character(round(prop_missing,3)), "%" ))  

synergy_abs_mgkg %>%
  count(premises_id)

synergy_abs_mgkg <- synergy_abs_mgkg %>%
  mutate(premises_id = as.factor(as.character(premises_id)))

setwd(path)
saveRDS(synergy_abs_mgkg, "amu/synergy_abs_mgkg.Rds")
```

```{r}
unique(synergy_abs_mgkg$premises_id)[1:15]

synergy_abs_mgkg %>%
  count(premises_id)

# 129 premises

synergy_abs_mgkg <- synergy_abs_mgkg %>%
  select(Region, Id, premises_id, sale_id, visit_id, month, date, vet_id, abs_id, med_name, species, form, active_sub, med_group, abs_class, num_ingred, conc, conc_unit, quantity, quantity_unit, denom_unit, unit_correction, rolling_12_month_av,  herd_av_kg,
         mg_abs, abs_mg_kg) %>%
  rename("region" = "Region",
         "interherd_ID" = "Id")
  


hpcia_list <- c("3rd generation Cephalosporin",
                "4th generation Cephalosporin",
                "Fluoroquinolone")

synergy_abs_mgkg <- synergy_abs_mgkg %>%
  mutate(abs_class = as.factor(str_trim(abs_class)),
         med_name = as.factor(med_name),
         hpcia = ifelse(abs_class %in% c(hpcia_list), 1, 0))
# 353262 rows, 26 cols



synergy_abs_mgkg <- synergy_abs_mgkg %>%
  distinct() 
# 353262 rows, 26 cols

dim(synergy_abs_mgkg)

setwd(path)

saveRDS(synergy_abs_mgkg, "amu/synergy_abs_mgkg.Rds")
```

```{r}
synergy_abs_mgkg %>%
   # filter(premises_id == "1023") %>%
  group_by(month) %>%
  summarise(total_amu = sum(abs_mg_kg)) %>%
  ggplot() +
  geom_line(aes(x = month, y = total_amu))
  
synergy_abs_mgkg %>%
  count(premises_id)
synergy_abs_mgkg %>%
  filter(premises_id == "1023") %>%
  count(month, visit_id) %>%
  mutate(n = 1) %>%
  group_by(month) %>%
  summarise(visits = sum(n)) %>%
  ggplot() +
  geom_line(aes(x = month, y = visits))


synergy_abs_mgkg %>%
  filter(premises_id == "1023") %>%
 # filter(med_name == "Tetra-Delta Intramammary Suspension") %>%
  group_by(month) %>%
  summarise(total_amu = sum(abs_mg_kg)) %>%
  ggplot() +
  geom_line(aes(x = month, y = total_amu))

synergy_abs_mgkg %>%
  filter(premises_id == "1023") %>%
  filter(med_name == "Tetra-Delta Intramammary Suspension") %>%
  filter(date < "2017-11-01")

synergy_abs_mgkg %>%
  filter(premises_id == "1023") %>%
  filter(med_name == "Tetra-Delta Intramammary Suspension") %>%
  filter(date > "2017-11-01")
```

