---
title: "Model building - temperature effect part C"
output: html_notebook
---

Horseshoe prior model
Aim: variable selection to see which temperature and humidity related variables are best

Temperature - lags
Humidity = lags
Temp:humid interaction - lags
Below freezing - lags
Min temperature - lags
Max temperature - lags

+ Spline outside of horseshoe 

Plot - top variables - posterior dis and contours 
Table with full results and FDR

# Set-up
```{r}
library(tidyverse)
library(brms)
options(mc.cores = 8, brms.backend = "cmdstanr") # allows threading
library(tryCatchLog)
library(loo)
library(lubridate)
library(tidybayes)
```

# Paths
```{r}
datapath <- '/Users/lv13916/Library/CloudStorage/OneDrive-UniversityofBristol/Documents/PhD/projects/oh_star/data/rds_rda/modelling_uncertainty/data_with_locations/'
savepath <- '/Users/lv13916/Library/CloudStorage/OneDrive-UniversityofBristol/Documents/PhD/projects/oh_star/data/rds_rda/final_models_new/'
```


# Reading in data
```{r}
df1_yard_amox <- readRDS(paste0(datapath, 'df1_yard_', 'amox', '_brms.Rds'))
df1_shed_amox <- readRDS(paste0(datapath, 'df1_shed_', 'amox', '_brms.Rds'))
df1_yard_ceph <- readRDS(paste0(datapath, 'df1_yard_', 'ceph', '_brms.Rds'))
df1_shed_ceph <- readRDS(paste0(datapath, 'df1_shed_', 'ceph', '_brms.Rds'))
df1_yard_cipro <- readRDS(paste0(datapath, 'df1_yard_', 'cipro', '_brms.Rds'))
df1_shed_cipro <- readRDS(paste0(datapath, 'df1_shed_', 'cipro', '_brms.Rds'))
df1_yard_strep <- readRDS(paste0(datapath, 'df1_yard_', 'strep', '_brms.Rds'))
df1_shed_strep <- readRDS(paste0(datapath, 'df1_shed_', 'strep', '_brms.Rds'))
df1_yard_tetra <- readRDS(paste0(datapath, 'df1_yard_', 'tetra', '_brms.Rds'))
df1_shed_tetra <- readRDS(paste0(datapath, 'df1_shed_', 'tetra', '_brms.Rds'))

```


### Functions
```{r}
make_formula_horseshoe <- function(rf){
  
  count = 0
  rf_formula <- ''
  for (i in rf){
    if (count == 0){
      rf_formula <- paste(i)
    }
    if (count != 0) {
      rf_formula <- paste(rf_formula, '+', i)
    }
    count = count + 1
  }
  
  model_formula <- bf(count ~ main + am * log_inv_logit(riskfactors + re),nl=TRUE)
  model_formula <- model_formula + lf(main ~ offset(log_dilution) + (1|assay)) 
  model_formula <- model_formula + lf('re ~  1 + s(study_day_effect, bs ="gp") + (1|location_id) + (1|farm) + (1|assay)')
  model_formula <- model_formula + lf(paste("riskfactors ~ ", rf_formula))
  
  return(model_formula)
}

run_possion_model_horseshoe <- function(data, model_formula, savepath, savename){
    chain_length <- 4000
    custom_priors_highvar <- c(
      set_prior("horseshoe(1)", class= 'b', nlpar = 'riskfactors'), # horseshoe prior
      set_prior('normal(0, 5)', class = 'b', nlpar = 'main'), # weak info prior
      set_prior('normal(10, 1)', class = 'sd', nlpar = 're', group = 'assay'), # prevents this wide prior on 'true' random effects which we want with low var
      set_prior('normal(10, 1)', class = 'sd', nlpar = 'main')# fix variance high using normal dist
    )
    
  start_time <- Sys.time()
  
  options(mc.cores = 8, brms.backend = "cmdstanr") # allows threading

  model <- brm(
    formula = model_formula,
    data = as.data.frame(data), 
    family = poisson(), 
    prior = custom_priors_highvar,
    iter = chain_length, warmup = chain_length/2, chains = 4, cores = 4,
    silent = T,
    backend = "cmdstanr",
    threads = threading(2) #8 cores used 
    )
  
  end_time <- Sys.time()
  print(end_time - start_time)
  
  saveRDS(model, paste0(savepath, savename))
  
  return(model)
}

run_non_horseshoe_model <- function(df, save_name){
  model <- tryLog(run_possion_model(data = df,
                  model_formula = make_formula_poisson_var('mean_week_humidity_S + mean_2week_humidity_S + mean_4week_humidity_S + below_freezing_1week + below_freezing_2week + below_freezing_4week + minimum_temperature_1week_S + maximum_temperature_1week_S + mean_week_temperature_S + mean_2week_temperature_S + mean_4week_temperature_S + mean_week_temperature_S * mean_week_humidity_S + mean_2week_temperature_S * mean_2week_humidity_S + mean_4week_temperature_S * mean_4week_humidity_S + s(study_day_effect, bs ="gp") + (1|location_id) + (1|farm) + (1|assay)'),
                  savepath,
                  savename = paste0('non_horseshoe_model', save_name, '.Rds'),
                  chain_length = 4000))
  return(summary(model))
  rm(model)
}

run_non_horseshoe_model(df1_yard_ceph, 'yard_ceph')
```

### Running horseshoe prior model
```{r}
rf_list <- c(
  'mean_week_humidity_S',
  'mean_2week_humidity_S',
  'mean_4week_humidity_S',
  'below_freezing_1week',
  'below_freezing_2week',
  'below_freezing_4week',
  'minimum_temperature_1week_S',
  'maximum_temperature_1week_S',
  'mean_week_temperature_S',
  'mean_2week_temperature_S',
  'mean_4week_temperature_S',
  'mean_week_temperature_S*mean_week_humidity_S',
  'mean_2week_temperature_S*mean_2week_humidity_S',
  'mean_4week_temperature_S*mean_4week_humidity_S')

rf<- make_formula_horseshoe(rf_list)
rf
rf_list
# Amox

run_horseshoe <- function(df, name, rf_formula){
  horseshoe_model <- tryLog(
                            run_possion_model_horseshoe(
                              data = df,
                              model_formula = rf_formula,
                              savepath, savename = paste0('horseshoe_C1_', name, '.Rds')))
  
  summary(horseshoe_model)
  rm(horseshoe_model)
}



run_horseshoe(df1_yard_amox, 'yard_amox', rf)
run_horseshoe(df1_shed_amox, 'shed_amox', rf)

run_horseshoe(df1_yard_ceph, 'yard_ceph', rf)
run_horseshoe(df1_shed_ceph, 'shed_ceph', rf)

run_horseshoe(df1_yard_strep, 'yard_strep', rf)
run_horseshoe(df1_shed_strep, 'shed_strep', rf)

run_horseshoe(df1_yard_tetra, 'yard_tetra', rf)
run_horseshoe(df1_shed_tetra, 'shed_tetra', rf)


```


### Read in models
```{r}
amox_yardhorseshoe_C1 <- readRDS(paste0(savepath, 'horseshoe_C1_yard_amox.rds'))
amox_shedhorseshoe_C1 <- readRDS(paste0(savepath, 'horseshoe_C1_shed_amox.rds'))
ceph_yardhorseshoe_C1 <- readRDS(paste0(savepath, 'horseshoe_C1_yard_ceph.Rds'))
ceph_shedhorseshoe_C1 <- readRDS(paste0(savepath, 'horseshoe_C1_shed_ceph.Rds'))
strep_yardhorseshoe_C1 <- readRDS(paste0(savepath, 'horseshoe_C1_yard_strep.Rds'))
strep_shedhorseshoe_C1 <- readRDS(paste0(savepath, 'horseshoe_C1_shed_strep.Rds'))
tetra_yardhorseshoe_C1 <- readRDS(paste0(savepath, 'horseshoe_C1_yard_tetra.Rds'))
tetra_shedhorseshoe_C1 <- readRDS(paste0(savepath, 'horseshoe_C1_shed_tetra.Rds'))

summary(amox_yardhorseshoe_C1)
summary(tetra_shedhorseshoe_C1)
```

```{r, fig.height = 6, fig.width = 5}
median_and_CIs <- function(data){
  med <- as.character(round(median(data), 3))
  upp <- as.character(round(quantile(data, 0.975), 3))
  low <- as.character(round(quantile(data, 0.025), 3))
  sig <- ' '
  if((upp > 0 & low > 0) | (upp < 0 & low < 0) ){
    sig <- '*'
  }
  
  return(paste0(med, ' (', low, ', ', upp, ')  ', sig))
}

get_fdr <- function(model, am, location){
  res <- model %>%
    spread_draws(`b_riskfactors.*`, regex = T) %>%
    select(-.chain, -.iteration, -.draw, -b_riskfactors_Intercept) %>%
    gather(key = 'variable', value = 'estimate') %>%
    mutate(variable = gsub('b_riskfactors.', '', variable),
           estimate_grouped = ifelse(estimate > 0, 1, 0))
  
  fdr_res <- res %>%
    group_by(variable) %>%
    summarise(prop_estimate = mean(estimate_grouped),
              fdr = ifelse(prop_estimate < 0.5, prop_estimate, 1-prop_estimate),
              coef_estimate = median_and_CIs(estimate),
              med = median(estimate),
              low = quantile(estimate, 0.025),
              upp =  quantile(estimate, 0.975)) %>%
    arrange(fdr) %>%
    mutate(global_fdr = cummean(fdr),
           am = as.factor(am),
           location = as.factor(location))
  
  return(fdr_res)
}

get_draws_and_fdr <- function(model, am, location){
  res <- model %>%
    spread_draws(`b_riskfactors.*`, regex = T) %>%
    select(-.chain, -.iteration, -.draw, -b_riskfactors_Intercept) %>%
    gather(key = 'variable', value = 'estimate') %>%
    mutate(variable = as.factor(gsub('b_riskfactors.', '', variable)),
           estimate_grouped = ifelse(estimate > 0, 1, 0))
  
  fdr <- res %>%
    group_by(variable) %>%
    summarise(prop_estimate = mean(estimate_grouped),
              fdr = ifelse(prop_estimate < 0.5, prop_estimate, 1-prop_estimate)) %>%
    arrange(fdr) %>%
    mutate(global_fdr = cummean(fdr),
           am = as.factor(am),
           location = as.factor(location))
  
  res_and_fdr <- res %>%
    left_join(fdr, by = 'variable')
  
  return(res_and_fdr)
}

all_fdr <- rbind(get_fdr(amox_yardhorseshoe_C1, 'amox', 'yard'),
                 get_fdr(amox_shedhorseshoe_C1, 'amox', 'shed'),
                  get_fdr(ceph_yardhorseshoe_C1, 'ceph', 'yard'),
                  get_fdr(ceph_shedhorseshoe_C1, 'ceph', 'shed'),
                 get_fdr(strep_yardhorseshoe_C1, 'strep', 'yard'),
                 get_fdr(strep_shedhorseshoe_C1, 'strep', 'shed'),
                 get_fdr(tetra_yardhorseshoe_C1, 'tetra', 'yard'),
                 get_fdr(tetra_shedhorseshoe_C1, 'tetra', 'shed'))
all_fdr
get_fdr(strep_shedhorseshoe_C1, 'strep', 'shed')

fdr_res_table <- all_fdr %>%
  mutate(prop_estimate = round(prop_estimate, 3),
         fdr  = round(fdr, 3),
         global_fdr  = round(global_fdr, 3))

write.csv(fdr_res_table, paste0(savepath, 'fdr_horseshoe_model.csv'))

plot_horseshoe_results <- function(model, am_name, am_name_full, location_name, location_name_full, cutoff, n){
  
  model_fdr_draws <- get_draws_and_fdr(model, am_name, location_name)
  
  top5 <- as.character(get_fdr(model, am_name, location_name)$variable[1:n])
  
  model_fdr_draws <- model_fdr_draws %>%
    filter(variable %in% c(top5))
  
  levels(model_fdr_draws$variable) <- c('Freezing (7)', 'Freezing (14)', 'Freezing (28)',
                                        'Maximum temp.', 'Humidity (14)', 'Interaction (14)',
                                        'Temp. (14)', 'Humidity (28)', 'Interaction (28)',
                                        'Temp. (28)', 'Humidity (7)', 'Interaction (7)',
                                        'Temp. (7)', 'Minimum temp.')
  
    
  model_fdr_draws <- model_fdr_draws %>%
    mutate(fdr_sig = ifelse(global_fdr < cutoff, 'sig', 'no_sig'),
           variable = as.character(variable)) %>%
    arrange(-global_fdr)
  
  model_fdr_draws %>%
    ggplot() +
    stat_halfeye(aes(x = estimate, y = reorder(variable, -global_fdr), fill = fdr_sig), color = 'black') +
    geom_vline(aes(xintercept = 0), linetype = 2, colour = 'grey') +
    theme_minimal() +
    xlab('Coefficient estimate') +
    ylab('Predictor (ordered by FDR)') +
    scale_colour_manual(values = c(dual_blues[2], dual_greens[2])) +
    scale_fill_manual(values = c(dual_blues[2], dual_greens[2]), name = 'Global FDR',
                      labels = c(paste0('>=', as.character(cutoff)), paste0('<', as.character(cutoff)))) +
    ggtitle(paste0(am_name_full, ': ', location_name_full)) 

}


plot_non_horseshoe_results <- function(model, am_name, am_name_full, location_name, location_name_full, cutoff, n){
  
  model_fdr_draws <- get_draws_and_fdr_non_HS(model, am_name, location_name)
  
  top5 <- as.character(get_fdr_non_HS(model, am_name, location_name)$variable[1:n])
  
  model_fdr_draws <- model_fdr_draws %>%
    filter(variable %in% c(top5))
  
  levels(model_fdr_draws$variable) <- c('Freezing (7)', 'Freezing (14)', 'Freezing (28)',
                                        'Maximum temp.', 'Humidity (14)', 'Interaction (14)',
                                        'Temp. (14)', 'Humidity (28)', 'Interaction (28)',
                                        'Temp. (28)', 'Humidity (7)', 'Interaction (7)',
                                        'Temp. (7)', 'Minimum temp.')
  
    
  model_fdr_draws <- model_fdr_draws %>%
    mutate(fdr_sig = ifelse(global_fdr < cutoff, 'sig', 'no_sig'),
           variable = as.character(variable)) %>%
    arrange(-global_fdr)
  
  model_fdr_draws %>%
    ggplot() +
    stat_halfeye(aes(x = estimate, y = reorder(variable, -global_fdr), fill = fdr_sig), color = 'black') +
    geom_vline(aes(xintercept = 0), linetype = 2, colour = 'grey') +
    theme_minimal() +
    xlab('Coefficient estimate') +
    ylab('Predictor (ordered by FDR)') +
    scale_colour_manual(values = c(dual_blues[2], dual_greens[2])) +
    scale_fill_manual(values = c(dual_blues[2], dual_greens[2]), name = 'Global FDR',
                      labels = c(paste0('>=', as.character(cutoff)), paste0('<', as.character(cutoff)))) +
    ggtitle(paste0(am_name_full, ': ', location_name_full)) 

}


get_draws_and_fdr_non_HS <- function(model, am, location){
  res <- model %>%
    spread_draws(`b_interaction.*`, regex = T) %>%
    select(-.chain, -.iteration, -.draw, -b_interaction_Intercept) %>%
    gather(key = 'variable', value = 'estimate') %>%
    mutate(variable = as.factor(gsub('b_riskfactors.', '', variable)),
           estimate_grouped = ifelse(estimate > 0, 1, 0))
  
  fdr <- res %>%
    group_by(variable) %>%
    summarise(prop_estimate = mean(estimate_grouped),
              fdr = ifelse(prop_estimate < 0.5, prop_estimate, 1-prop_estimate)) %>%
    arrange(fdr) %>%
    mutate(global_fdr = cummean(fdr),
           am = as.factor(am),
           location = as.factor(location))
  
  res_and_fdr <- res %>%
    left_join(fdr, by = 'variable')
  
  return(res_and_fdr)
}


get_fdr_non_HS <- function(model, am, location){
  res <- model %>%
    spread_draws(`b_interaction.*`, regex = T) %>%
    select(-.chain, -.iteration, -.draw, -b_interaction_Intercept) %>%
    gather(key = 'variable', value = 'estimate') %>%
    mutate(variable = gsub('b_riskfactors.', '', variable),
           estimate_grouped = ifelse(estimate > 0, 1, 0))
  
  fdr_res <- res %>%
    group_by(variable) %>%
    summarise(prop_estimate = mean(estimate_grouped),
              fdr = ifelse(prop_estimate < 0.5, prop_estimate, 1-prop_estimate),
              coef_estimate = median_and_CIs(estimate),
              med = median(estimate),
              low = quantile(estimate, 0.025),
              upp =  quantile(estimate, 0.975)) %>%
    arrange(fdr) %>%
    mutate(global_fdr = cummean(fdr),
           am = as.factor(am),
           location = as.factor(location))
  
  return(fdr_res)
}
```

```{r, fig.height = 6, fig.width = 6}


plot_horseshoe_results(readRDS(paste0(savepath, 'horseshoe_C1_yard_amox.rds')), 'amox', 'Amoxicillin', 'yard', 'Adults in collecting yard', cutoff = 0.1, 5)
plot_horseshoe_results(readRDS(paste0(savepath, 'horseshoe_C1_shed_amox.rds')), 'amox', 'Amoxicillin', 'shed', 'Heifers in sheds/pens', cutoff = 0.1, 5)
plot_horseshoe_results(readRDS(paste0(savepath, 'horseshoe_C1_yard_ceph.Rds')), 'ceph', 'Cephalexin', 'shed', 'Adults in collecting yard', cutoff = 0.1, 5)
plot_horseshoe_results(readRDS(paste0(savepath, 'horseshoe_C1_shed_ceph.Rds')), 'ceph', 'Cephalexin', 'yard', 'Heifers in sheds/pens', cutoff = 0.1, 5)
plot_horseshoe_results(readRDS(paste0(savepath, 'horseshoe_C1_yard_strep.Rds')), 'strep', 'Streptomycin', 'shed', 'Adults in collecting yard', cutoff = 0.1, 5)
plot_horseshoe_results(readRDS(paste0(savepath, 'horseshoe_C1_shed_strep.Rds')), 'strep', 'Streptomycin', 'yard', 'Heifers in sheds/pens', cutoff = 0.1, 10)
plot_horseshoe_results(readRDS(paste0(savepath, 'horseshoe_C1_yard_tetra.Rds')), 'tetra', 'Tetracycline', 'shed', 'Adults in collecting yard', cutoff = 0.1, 5)
plot_horseshoe_results(readRDS(paste0(savepath, 'horseshoe_C1_shed_tetra.Rds')), 'strep', 'Tetracycline', 'yard', 'Heifers in sheds/pens', cutoff = 0.1, 5)

non_horseshoe <-readRDS(paste0(savepath, 'non_horseshoe_modelyard_ceph.Rds'))
plot_non_horseshoe_results(non_horseshoe, 'ceph', 'Non-HS: Cephalexin', 'yard', 'Adults in collecting yard', cutoff = 0.1, 14)
plot_horseshoe_results(readRDS(paste0(savepath, 'horseshoe_C1_yard_ceph.rds')), 'ceph', 'Cephalexin', 'yard', 'Adults in collecting yard', cutoff = 0.1, 14)

get_variables(non_horseshoe)

```

```{r, fig.height =5, fig.width= 6}
  #values = c('Amoxicillin' = "#0CC6DE", 'Cephalexin' = "#024731",  'Ciprofloxacin' = "#34B233", 'Streptomycin' ="#002F5F", 'Tetracycline' ='#9672b5')) +

plot_horseshoe_contours(readRDS(paste0(savepath, 'horseshoe_C1_yard_amox.rds')), 'amox', 'yard', n =3, '#0CC6DE')
plot_horseshoe_contours(readRDS(paste0(savepath, 'horseshoe_C1_shed_amox.rds')), 'amox',  'shed', n = 3, '#0CC6DE')

plot_horseshoe_contours(readRDS(paste0(savepath, 'horseshoe_C1_yard_ceph.Rds')), 'ceph',  'shed',  n = 4, '#34B233')
plot_horseshoe_contours(readRDS(paste0(savepath, 'horseshoe_C1_shed_ceph.Rds')), 'ceph',  'yard',  n = 3, '#34B233')

plot_horseshoe_contours(readRDS(paste0(savepath, 'horseshoe_C1_yard_strep.Rds')), 'strep',  'shed',  n = 3,'#002F5F')
#plot_horseshoe_contours(readRDS(paste0(savepath, 'horseshoe_C1_shed_strep.Rds')), 'strep', 'yard',  n = 5, '#002F5F')

plot_horseshoe_contours(readRDS(paste0(savepath, 'horseshoe_C1_yard_tetra.Rds')), 'tetra',  'shed',  n = 3, '#9672b5')
plot_horseshoe_contours(readRDS(paste0(savepath, 'horseshoe_C1_shed_tetra.Rds')), 'strep',  'yard',  n = 3, '#9672b5')


p1 <-plot_horseshoe_contours_NON_HS(readRDS(paste0(savepath, 'non_horseshoe_modelyard_ceph.Rds')), 'ceph',  'yard',  n = 5, '#024731')
p2 <-plot_horseshoe_contours(readRDS(paste0(savepath, 'horseshoe_C1_shed_ceph.Rds')), 'ceph',  'yard',  n = 5, '#34B233')

p1
p2

```

```{r}
plot_spline_day_of_study <- function(model, data, no_bacs, am_name, location_name, colour_code, min_date, max_date){
    
  n <- 100
  seq_day_in_study <- seq(0,1,(1/(n-1)))
  
  dummy_data <- tibble(
    x_val = rep(paste0('V', as.character(seq(1,n))), 2)) %>%
    mutate(am = c(rep(0, n), rep(1, n)),
           log_dilution = c(rep(log(0.1),n), rep(0, n)),
           mean_week_temperature_S = 0,
           mean_2week_temperature_S = 0,
           mean_4week_temperature_S = 0,
           mean_week_humidity_S = 0,
           mean_2week_humidity_S = 0,
           mean_4week_humidity_S = 0,
           below_freezing_1week = 0.5,
           below_freezing_2week = 0.5,
           below_freezing_4week = 0.5,
           minimum_temperature_1week_S = 0,
           maximum_temperature_1week_S = 0,
           study_day_effect = rep(seq_day_in_study, 2),
           farm = NA,
           assay = NA,
           location_id = NA)
  
  estimates <- as_tibble(inv_logit_scaled(fitted(model,
                      newdata = dummy_data,
                      re_formula = NA,
                      nlpar = 're')))
  
  assays <- as_tibble(inv_logit_scaled(fitted(model,
                      re_formula = NULL,
                      nlpar = 're')))
  
  names(assays) <- paste0('assay_', names(assays))
  
  n_days <- as.numeric(max(data$date) - min(data$date))
  
  assays_ests <- cbind(assays, model$data) %>%
    filter(am == 0) %>%
    mutate(date = min(data$date) + study_day_effect*n_days)

  res <- cbind(estimates, dummy_data) %>%
    filter(am == 0) %>%
    filter(study_day_effect > min(assays_ests$study_day_effect) & study_day_effect < max(assays_ests$study_day_effect)) %>%
    mutate(date = min(data$date) + study_day_effect*n_days)
  
  diff <- (min(res$Estimate)) /median(assays_ests$assay_Estimate) # no intercept, so adjust spline to median

  spline_plot <- res %>%
    ggplot() +
    geom_point(data = no_bacs, aes(y = min(assays_ests$assay_Estimate), x = date), alpha = 0.5, colour = 'red', shape = 18, size = 2.5) +
    geom_point(data = assays_ests, aes(y = assay_Estimate, x = date), alpha = 0.3, colour = 'grey') +
    geom_line(aes(x = date, y = Estimate/diff), colour = colour_code, size = 1.5) +
    geom_ribbon(aes(x =  date, ymin = Q2.5/diff, ymax = Q97.5/diff), alpha = 0.5, fill = colour_code) +
    scale_y_continuous(trans = 'log10') +
    xlab('Date') +
    ylab('Estimated proportion resistant') +
    theme_minimal() +
    ggtitle(paste0(am_name, ': ', location_name))
  
  return(spline_plot)
  
}

names(amox_yardhorseshoe_C1$data)
```




```{r}
no_bac_yard <- readRDS(paste0(datapath, 'df1_no_bac_yard.Rds'))
no_bac_shed <- readRDS(paste0(datapath, 'df1_no_bac_shed.Rds'))

df1_yard_amox <- readRDS(paste0(datapath, 'df1_yard_', 'amox', '_brms.Rds'))
df1_shed_amox <- readRDS(paste0(datapath, 'df1_shed_', 'amox', '_brms.Rds'))
df1_yard_ceph <- readRDS(paste0(datapath, 'df1_yard_', 'ceph', '_brms.Rds'))
df1_shed_ceph <- readRDS(paste0(datapath, 'df1_shed_', 'ceph', '_brms.Rds'))
df1_yard_strep <- readRDS(paste0(datapath, 'df1_yard_', 'strep', '_brms.Rds'))
df1_shed_strep <- readRDS(paste0(datapath, 'df1_shed_', 'strep', '_brms.Rds'))
df1_yard_tetra <- readRDS(paste0(datapath, 'df1_yard_', 'tetra', '_brms.Rds'))
df1_shed_tetra <- readRDS(paste0(datapath, 'df1_shed_', 'tetra', '_brms.Rds'))

all_data <- rbind(df1_yard_amox, df1_shed_amox)
min_date <- min(all_data$date)
max_date <- max(all_data$date)

p_amox_yard <- plot_spline_day_of_study(readRDS(paste0(savepath, 'horseshoe_C1_yard_amox.rds')),
                         df1_yard_amox, no_bac_yard, 'Amoxicillin', 'Adults in collecting yard', '#0CC6DE',
                         min_date, max_date)



p_amox_shed <- plot_spline_day_of_study(readRDS(paste0(savepath, 'horseshoe_C1_shed_amox.rds')),
                         df1_yard_amox, no_bac_shed, 'Amoxicillin', 'Heifers in sheds/pens', '#0CC6DE',
                         min_date, max_date)

p_ceph_yard <- plot_spline_day_of_study(readRDS(paste0(savepath, 'horseshoe_C1_yard_ceph.rds')),
                         df1_yard_amox, no_bac_yard, 'Cephalexin', 'Adults in collecting yard', '#34B233',
                         min_date, max_date)

p_ceph_shed <- plot_spline_day_of_study(readRDS(paste0(savepath, 'horseshoe_C1_shed_ceph.rds')),
                         df1_yard_amox, no_bac_shed, 'Cephalexin', 'Heifers in sheds/pens', '#34B233',
                         min_date, max_date)

p_strep_yard <- plot_spline_day_of_study(readRDS(paste0(savepath, 'horseshoe_C1_yard_strep.rds')),
                         df1_yard_amox, no_bac_yard, 'Streptomycin', 'Adults in collecting yard', '#002F5F',
                         min_date, max_date)

p_strep_shed <- plot_spline_day_of_study(readRDS(paste0(savepath, 'horseshoe_C1_shed_strep.rds')),
                         df1_yard_amox, no_bac_shed, 'Streptomycin', 'Heifers in sheds/pens', '#002F5F',
                         min_date, max_date)


p_tetra_yard <- plot_spline_day_of_study(readRDS(paste0(savepath, 'horseshoe_C1_yard_tetra.rds')),
                         df1_yard_amox, no_bac_yard, 'Tetracycline', 'Adults in collecting yard', '#9672b5',
                         min_date, max_date)

p_tetra_shed <- plot_spline_day_of_study(readRDS(paste0(savepath, 'horseshoe_C1_shed_tetra.rds')),
                         df1_yard_amox, no_bac_shed, 'Tetracycline', 'Heifers in sheds/pens', '#9672b5',
                         min_date, max_date)
```

```{r, fig.width = 5, fig.height = 4}
p_amox_yard
p_amox_shed

p_ceph_yard
p_ceph_shed

p_strep_yard
p_strep_shed

p_tetra_yard
p_tetra_shed
```


```{r, fig.width = 5, fig.height = 5}

plot_horseshoe_contours <- function(model, am_name, location_name, n, colour_code) {
  
  fdr <- get_fdr(model, am_name, location_name)
  top <- as.character(fdr$variable[1:n])
  
  just_fdr <- fdr %>%
    filter(variable %in% top) %>%
    mutate(variable_name = paste0('var_', seq(1,n))) %>%
    select(variable, variable_name, fdr)
   
  all_draws <- model %>%
    spread_draws(`b_riskfactors.*`, regex = T) %>%
    select(-.chain, -.iteration, -.draw) %>%
    gather(key = 'variable', value ='estimate') %>%
    mutate(variable = gsub('b_riskfactors_', '', variable)) %>%
    left_join(just_fdr, by = 'variable') %>%
    filter(!is.na(variable_name)) %>%
    mutate(variable_name = as.factor(variable_name)) %>%
    select(-variable, - fdr)
  
  all_draws <- all_draws %>%
    mutate(id = rep(seq(1, 8000), n)) %>%
    spread(key = 'variable_name', value = 'estimate')
  
  p_blank <- ggplot() +
    theme_minimal()
  
  p1 <- all_draws %>%
    ggplot() +
    geom_density_2d(aes(y = var_1, x = var_2), colour = colour_code) +
    geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
    geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
    theme_minimal() +
    xlab('') +
    ylab('')
  
  p2 <- all_draws %>%
    ggplot() +
    geom_density_2d(aes(y = var_1, x = var_3), colour = colour_code) +
    geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
    geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
    theme_minimal() +
    xlab('') +
    ylab('')
  
  if (n >= 4){
  p3 <- all_draws %>%
    ggplot() +
    geom_density_2d(aes(y = var_1, x = var_4), colour = colour_code) +
    geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
    geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
    theme_minimal() +
    xlab('') +
    ylab('')
  } else{
    p3 <- p_blank
  }
  
  if (n >= 5){
    p4 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_1, x = var_5), colour = colour_code) +
    geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
    geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p4 <- p_blank
  }
  
  
  p5 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_2, x = var_3), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  
  
  if (n >= 4){
    p6 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_2, x = var_4), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
    }else{
      p6 <- p_blank
  }
    
  if (n >= 5){
    p7 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_2, x = var_5), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p7 <- p_blank
  }
  
  if (n >= 4){  
    p8 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_3, x = var_4), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p8 <- p_blank
  }
     
  if (n >= 5){ 
    p9 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_3, x =  var_5), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p9 <- p_blank
  }    
  
  if (n >= 5){
    p10 <-  all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_4, x = var_5), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p10 <- p_blank
  }
  
  if(n == 3){
    gridExtra::grid.arrange(p1, p2,
                            p_blank, p5, 
                            nrow = 2)
  }
  
  if(n == 4){
    gridExtra::grid.arrange(p1, p2, p3,
                          p_blank, p5, p6,
                          p_blank, p_blank, p8,
                          nrow = 3)
  }
  
  if(n == 5){
    gridExtra::grid.arrange(p1, p2, p3, p4,
                          p_blank, p5, p6, p7,
                          p_blank, p_blank, p8, p9,
                          p_blank,p_blank,p_blank,p10,
                          nrow = 4)
  }
  
}
#values = c('Amoxicillin' = "#0CC6DE", 'Cephalexin' = "#024731",  'Ciprofloxacin' = "#34B233", 'Streptomycin' ="#002F5F", 'Tetracycline' ='#9672b5')) +


plot_horseshoe_contours_NON_HS <- function(model, am_name, location_name, n, colour_code) {
  
  fdr <- get_fdr_non_HS(model, am_name, location_name)
  top <- as.character(fdr$variable[1:n])
  
  just_fdr <- fdr %>%
    filter(variable %in% top) %>%
    mutate(variable_name = paste0('var_', seq(1,n))) %>%
    select(variable, variable_name, fdr)
   
  all_draws <- model %>%
    spread_draws(`b_interaction.*`, regex = T) %>%
    select(-.chain, -.iteration, -.draw, -b_interaction_Intercept) %>%
    gather(key = 'variable', value ='estimate') %>%
    mutate(variable = gsub('b_riskfactors_', '', variable)) %>%
    left_join(just_fdr, by = 'variable') %>%
    filter(!is.na(variable_name)) %>%
    mutate(variable_name = as.factor(variable_name)) %>%
    select(-variable, - fdr)
  
  all_draws <- all_draws %>%
    mutate(id = rep(seq(1, 8000), n)) %>%
    spread(key = 'variable_name', value = 'estimate')
  
  p_blank <- ggplot() +
    theme_minimal()
  
  p1 <- all_draws %>%
    ggplot() +
    geom_density_2d(aes(y = var_1, x = var_2), colour = colour_code) +
    geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
    geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
    theme_minimal() +
    xlab('') +
    ylab('')
  
  p2 <- all_draws %>%
    ggplot() +
    geom_density_2d(aes(y = var_1, x = var_3), colour = colour_code) +
    geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
    geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
    theme_minimal() +
    xlab('') +
    ylab('')
  
  if (n >= 4){
  p3 <- all_draws %>%
    ggplot() +
    geom_density_2d(aes(y = var_1, x = var_4), colour = colour_code) +
    geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
    geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
    theme_minimal() +
    xlab('') +
    ylab('')
  } else{
    p3 <- p_blank
  }
  
  if (n >= 5){
    p4 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_1, x = var_5), colour = colour_code) +
    geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
    geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p4 <- p_blank
  }
  
  
  p5 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_2, x = var_3), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  
  
  if (n >= 4){
    p6 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_2, x = var_4), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
    }else{
      p6 <- p_blank
  }
    
  if (n >= 5){
    p7 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_2, x = var_5), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p7 <- p_blank
  }
  
  if (n >= 4){  
    p8 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_3, x = var_4), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p8 <- p_blank
  }
     
  if (n >= 5){ 
    p9 <- all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_3, x =  var_5), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p9 <- p_blank
  }    
  
  if (n >= 5){
    p10 <-  all_draws %>%
      ggplot() +
      geom_density_2d(aes(y = var_4, x = var_5), colour = colour_code) +
      geom_vline(aes(xintercept = 0),  colour = 'darkgrey') +
      geom_hline(aes(yintercept = 0),  colour = 'darkgrey') +
      theme_minimal() +
      xlab('') +
      ylab('')
  }else{
      p10 <- p_blank
  }
  
  if(n == 3){
    gridExtra::grid.arrange(p1, p2,
                            p_blank, p5, 
                            nrow = 2)
  }
  
  if(n == 4){
    gridExtra::grid.arrange(p1, p2, p3,
                          p_blank, p5, p6,
                          p_blank, p_blank, p8,
                          nrow = 3)
  }
  
  if(n == 5){
    gridExtra::grid.arrange(p1, p2, p3, p4,
                          p_blank, p5, p6, p7,
                          p_blank, p_blank, p8, p9,
                          p_blank,p_blank,p_blank,p10,
                          nrow = 4)
  }
  
}
#values = c('Amoxicillin' = "#0CC6DE", 'Cephalexin' = "#024731",  'Ciprofloxacin' = "#34B233", 'Streptomycin' ="#002F5F", 'Tetracycline' ='#9672b5')) +


```