---
title: "Model building - temperature effect part A"
output: html_notebook
---

Part A
Split models for 'collecting yard' and 'heifers'
Univariable analysis

Predictors:
- Intercept only
- Spline to demonstrate seasonal effects
- Air temperature (1 week)
- Humidity (1 week)

Results - display as table only

# Set-up
```{r}
library(tidyverse)
library(brms)
options(mc.cores = 8, brms.backend = "cmdstanr") # allows threading
library(tryCatchLog)
library(loo)
library(lubridate)
library(tidybayes)
```

# Paths
```{r}
datapath <- '/Users/lv13916/Library/CloudStorage/OneDrive-UniversityofBristol/Documents/PhD/projects/oh_star/data/rds_rda/modelling_uncertainty/data_with_locations/'
savepath <- '/Users/lv13916/Library/CloudStorage/OneDrive-UniversityofBristol/Documents/PhD/projects/oh_star/data/rds_rda/final_models_new/'
```

# Functions
### Creating formula
```{r}
make_formula_poisson_var <- function(rf_formula){
  
  model_formula <- bf(count ~ main + am * log_inv_logit(interaction),nl=TRUE)
  model_formula <- model_formula + lf(main ~ offset(log_dilution) + (1|assay)) 
  model_formula <- model_formula + lf(paste("interaction ~ ", as.character(rf_formula)))
  
  return(model_formula)
}

```


### Computing model
```{r}
run_possion_model <- function(data, model_formula, savepath, savename, chain_length){
    if (is.na(chain_length)){
      chain_length <- 4000
    }
  
    custom_priors_highvar <- c(
      set_prior('normal(0, 5)', class = 'b', nlpar = 'interaction'), 
      set_prior('normal(0, 5)', class = 'b', nlpar = 'main'),
      set_prior('normal(10, 1)', class = 'sd', nlpar = 'interaction', group = 'assay'), # prevents this wide prior on 'true' random effects which we want with low var
      set_prior('normal(10, 1)', class = 'sd', nlpar = 'main')# fix variance high using normal dist
    )
    
  start_time <- Sys.time()
  
  options(mc.cores = 8, brms.backend = "cmdstanr") # allows threading

  model <- brm(
    formula = model_formula,
    data = as.data.frame(data), 
    family = poisson(), 
    prior = custom_priors_highvar,
    iter = chain_length, warmup = chain_length/2, chains = 4, cores = 4,
    silent = F,
    backend = "cmdstanr",
    threads = threading(2) #8 cores used 
    )
  
  end_time <- Sys.time()
  print(end_time - start_time)
  
  saveRDS(model, paste0(savepath, savename))
  
  return(model)
}

```

# Creating data
```{r}
create_split_data <- function(am_name){
  df1 <- readRDS(paste0(datapath, 'df1_', am_name, '_brms.Rds'))
  
  df1 <- df1 %>%
    mutate(study_day_effect = as.numeric(date - min(df1$date)))
  
  max_day <- max(df1$study_day_effect)
    
  df1 <- df1 %>%
    mutate(study_day_effect = (max_day - study_day_effect)/max_day)
  
  yard <- df1 %>%
    filter(location_age == 'collecting_yard_adult')
  
  shed <- df1 %>%
    filter(location_age == 'shed_pen_heifer')
  
  saveRDS(yard, paste0(datapath, 'df1_yard_', am_name, '_brms.Rds'))
  saveRDS(shed, paste0(datapath, 'df1_shed_', am_name, '_brms.Rds'))
}

# Amox
create_split_data('amox')
# Ceph
create_split_data('ceph')
# Cipro
create_split_data('cipro')
# Strep
create_split_data('strep')
# Tetra
create_split_data('tetra')

readRDS(paste0(datapath, 'df1_yard_', 'amox', '_brms.Rds'))
readRDS(paste0(datapath, 'df1_shed_', 'amox', '_brms.Rds'))

df1 <- readRDS(paste0(datapath, 'df1_', 'amox', '_brms.Rds'))
df1 %>%
  filter(plate == 'plain') %>%
  count(location_cat, age_cat)

mu_temp <- mean(df1$mean_week_temperature)
sd_temp <- sd(df1$mean_week_temperature)
mu_hum <- mean(df1$mean_week_humidity/100)
sd_hum  <- sd(df1$mean_week_humidity/100)

```


# Missing data
```{r, fig.width = 4, fig.height=2}
df1_with_no_bac_assays <- readRDS(paste0(datapath, 'df1_with_no_bac_assays.Rds'))
df1_yard_amox <- readRDS(paste0(datapath, 'df1_yard_', 'amox', '_brms.Rds'))
df1_shed_amox <- readRDS(paste0(datapath, 'df1_shed_', 'amox', '_brms.Rds'))

no_bac_yard <- df1_with_no_bac_assays %>%
  filter(assay %in% c(df1_yard_amox$assay))

no_bac_shed <- df1_with_no_bac_assays %>%
  filter(assay %in% c(df1_shed_amox$assay))

saveRDS(no_bac_yard, paste0(datapath, 'df1_no_bac_yard.Rds'))
saveRDS(no_bac_shed, paste0(datapath, 'df1_no_bac_shed.Rds'))

no_bac <- rbind(no_bac_yard, no_bac_shed)
df1_combined <- rbind(df1_yard_amox, df1_shed_amox) %>%
  filter(plate == 'plain')

no_bac %>%
  ggplot(aes(x = mean_week_temperature, y= log10p1(..count..))) +
  geom_histogram(data = df1_combined, alpha = 0.5) +
  geom_histogram(fill = 'red', alpha = 0.5) +
  theme_minimal()+
  xlab('Air temperature (celsius)')+
  ylab('Count (log10)')

no_bac %>%
  ggplot(aes(x = mean_week_humidity, y= log10p1(..count..))) +
  geom_histogram(data = df1_combined, alpha = 0.5) +
  geom_histogram(fill = 'red', alpha = 0.5) +
  theme_minimal() +
  xlab('Relative humidity (%)') +
  ylab('Count (log10)')

df1_with_no_bac_assays %>%
  count(location_cat)

df1_ceph_brms_just_plain %>%
  count(location_cat)
```
```{r}
df1_yard_amox_edit <- df1_yard_amox %>%
  filter(am ==0) %>%
  mutate(nearest_month = floor_date(date, unit = 'months')) %>%
  group_by(farm, nearest_month) %>%
  summarise(n = n(),
            mu_bac_abun = mean(count))
df1_shed_amox_edit <- df1_shed_amox  %>%
  filter(am ==0) %>%
  mutate(nearest_month = floor_date(date, unit = 'months')) %>%
  group_by(farm, nearest_month) %>%
  summarise(n = n(),
            mu_bac_abun = mean(count))

median(df1_yard_amox_edit$n)
median(df1_shed_amox_edit$n)

ggplot() +
  geom_line(data = df1_shed_amox_edit, aes(x = nearest_month, y = n), colour = dual_blues[2]) +
  geom_line(data = df1_yard_amox_edit, aes(x = nearest_month, y = n), colour = dual_greens[2]) 


ggplot() +
  geom_line(data = df1_shed_amox_edit, aes(x = nearest_month, y = mu_bac_abun), colour = dual_blues[2]) +
  geom_line(data = df1_yard_amox_edit, aes(x = nearest_month, y = mu_bac_abun), colour = dual_greens[2]) 

df1_yard_amox %>%
  mutate(month = month(date)) %>%
  filter(am == 0) %>%
  group_by(month) %>%
  summarise(mu_bac_abun = median(count))

df1_shed_amox %>%
  mutate(month = month(date)) %>%
  filter(am == 0) %>%
  group_by(month) %>%
  summarise(mu_bac_abun = median(count))

cor((df1_yard_amox %>% filter(am == 0))$count, (df1_yard_amox %>% filter(am == 0))$temperature_daily_mean) 
cor((df1_shed_amox %>% filter(am == 0))$count, (df1_shed_amox %>% filter(am == 0))$temperature_daily_mean) 

df1_shed_amox_edit

median((df1_shed_amox %>%
  group_by(farm) %>%
  summarise(min_date = min(date),
            max_date = max(date),
            diff = as.numeric(max_date - min_date)/365))$diff)

1.632877
1.213699
```

# Running intercept only
```{r}
run_intercept_only <- function(df, save_name){
  model <- tryLog(run_possion_model(data = df,
                  model_formula = make_formula_poisson_var('1 + (1|location_id) + (1|farm) + (1|assay)'),
                  savepath,
                  savename = paste0('int_only_A0_', save_name, '.Rds'),
                  chain_length = 2000))
  return(summary(model))
  rm(model)
}

df1_yard_amox <- readRDS(paste0(datapath, 'df1_yard_', 'amox', '_brms.Rds'))
df1_shed_amox <- readRDS(paste0(datapath, 'df1_shed_', 'amox', '_brms.Rds'))
df1_yard_ceph <- readRDS(paste0(datapath, 'df1_yard_', 'ceph', '_brms.Rds'))
df1_shed_ceph <- readRDS(paste0(datapath, 'df1_shed_', 'ceph', '_brms.Rds'))
df1_yard_cipro <- readRDS(paste0(datapath, 'df1_yard_', 'cipro', '_brms.Rds'))
df1_shed_cipro <- readRDS(paste0(datapath, 'df1_shed_', 'cipro', '_brms.Rds'))
df1_yard_strep <- readRDS(paste0(datapath, 'df1_yard_', 'strep', '_brms.Rds'))
df1_shed_strep <- readRDS(paste0(datapath, 'df1_shed_', 'strep', '_brms.Rds'))
df1_yard_tetra <- readRDS(paste0(datapath, 'df1_yard_', 'tetra', '_brms.Rds'))
df1_shed_tetra <- readRDS(paste0(datapath, 'df1_shed_', 'tetra', '_brms.Rds'))

run_intercept_only(df1_yard_amox, 'yard_amox')
run_intercept_only(df1_shed_amox, 'shed_amox')

run_intercept_only(df1_yard_ceph, 'yard_ceph')
run_intercept_only(df1_shed_ceph, 'shed_ceph')

run_intercept_only(df1_yard_cipro, 'yard_cipro')
run_intercept_only(df1_shed_cipro, 'shed_cipro')

run_intercept_only(df1_yard_strep, 'yard_strep')
run_intercept_only(df1_shed_strep, 'shed_strep')

run_intercept_only(df1_shed_tetra, 'shed_tetra')
run_intercept_only(df1_yard_tetra, 'yard_tetra')

```


# Running temp only
```{r}
run_temp_only <- function(df, save_name){
  model <- tryLog(run_possion_model(data = df,
                  model_formula = make_formula_poisson_var('mean_week_temperature_S + (1|location_id) + (1|farm) + (1|assay)'),
                  savepath,
                  savename = paste0('temp_only_A1_', save_name, '.Rds'),
                  chain_length = 2000))
  return(summary(model))
  rm(model)
}


run_temp_only(df1_yard_amox, 'yard_amox')
run_temp_only(df1_shed_amox, 'shed_amox')

run_temp_only(df1_yard_ceph, 'yard_ceph')
run_temp_only(df1_shed_ceph, 'shed_ceph')

run_temp_only(df1_yard_cipro, 'yard_cipro')
run_temp_only(df1_shed_cipro, 'shed_cipro')

run_temp_only(df1_yard_strep, 'yard_strep')
run_temp_only(df1_shed_strep, 'shed_strep')

run_temp_only(df1_shed_tetra, 'shed_tetra')
run_temp_only(df1_yard_tetra, 'yard_tetra')

```


# Running humidity only
```{r}
run_hum_only <- function(df, save_name){
  model <- tryLog(run_possion_model(data = df,
                  model_formula = make_formula_poisson_var('mean_week_humidity_S + (1|location_id) + (1|farm) + (1|assay)'),
                  savepath,
                  savename = paste0('hum_only_A2_', save_name, '.Rds'),
                  chain_length = 2000))
  return(summary(model))
  rm(model)
}


run_hum_only(df1_yard_amox, 'yard_amox')
run_hum_only(df1_shed_amox, 'shed_amox')

run_hum_only(df1_yard_ceph, 'yard_ceph')
run_hum_only(df1_shed_ceph, 'shed_ceph')

run_hum_only(df1_yard_cipro, 'yard_cipro')
run_hum_only(df1_shed_cipro, 'shed_cipro')

run_hum_only(df1_yard_strep, 'yard_strep')
run_hum_only(df1_shed_strep, 'shed_strep')

run_hum_only(df1_shed_tetra, 'shed_tetra')
run_hum_only(df1_yard_tetra, 'yard_tetra')

```







season_spline_plot <- function(model, data){
  
  model <- readRDS(paste0(save_collecting_yard_adult_ceph_model
  
  new_data <- collecting_yard_adult_ceph_model$data %>%
    mutate(assay = NA, farm = NA, location_id = NA,
           mean_week_temperature_S = 0,
           mean_week_humidity_S = 0)
           
  new_data
  estimates <- as_tibble(inv_logit_scaled(fitted(collecting_yard_adult_ceph_model,
                      newdata = new_data,
                      re_formula = NA,
                      nlpar = 'interaction')))
  
  assays <- as_tibble(inv_logit_scaled(fitted(collecting_yard_adult_ceph_model,
                      re_formula = NULL,
                      nlpar = 'interaction'))) %>%
    distinct()
  
  names(assays) <- paste0('assay_', names(assays))
  
  res <- cbind(estimates, collecting_yard_adult_ceph_model$data) %>%
    filter(am == 0)
  assays <- cbind(assays, collecting_yard_adult_ceph_model$data) %>%
    filter(am == 0)
  res
  assays
  final_res <- res %>%
    left_join(collecting_yard_adult_ceph, by = 'assay') %>%
    left_join(assays, by = 'assay') %>%
    distinct()
  
  spline_plot <- final_res %>%
    ggplot() +
    geom_line(aes(x = date, y = Estimate)) +
    geom_ribbon(aes(x =  date, ymin = Q2.5, ymax = Q97.5), alpha = 0.3) +
    geom_point(aes(y = assay_Estimate, x = date), alpha = 0.1) +
    scale_y_continuous(trans = 'log10') +
    xlab('Date') +
    ylab('Estimated proportion resistant')
  
  temp <- final_res %>%
    ggplot() +
    geom_line(aes(x = date, y = mean_week_temperature_S), colour = 'blue')
  
  humid <- final_res %>%
    ggplot() +
    geom_line(aes(x = date, y = mean_week_humidity_S), colour = 'green')
  
  gridExtra::grid.arrange(spline_plot, temp, humid, nrow = 3)
  
  spline_plot
  
}

collecting_yard_adult_ceph_model <- tryLog(run_possion_model(data = collecting_yard_adult_ceph,
                  model_formula = make_formula_poisson_var('mean_week_temperature_S + mean_week_humidity_S + s(study_day_effect, bs ="gp") + (1|location_id) + (1|farm) + (1|assay)'),
                  savepath,
                  savename = 'sep_agegroups_model1.Rds'))
summary(collecting_yard_adult_ceph_model)

shed_pen_heifer_ceph_model <- tryLog(run_possion_model(data = shed_pen_heifer_ceph,
                  model_formula = make_formula_poisson_var('mean_week_temperature_S + mean_week_humidity_S + s(study_day_effect, bs ="gp") + (1|location_id) + (1|farm) + (1|assay)'),
                  savepath,
                  savename = 'sep_agegroups_model2.Rds'))

adults_only_ceph_model <- tryLog(run_possion_model(data = adults_only_ceph,
                  model_formula = make_formula_poisson_var('mean_week_temperature_S:location_cat + mean_week_temperature_S + location_cat + s(study_day_effect, bs ="gp") + (1|location_id) + (1|farm) + (1|assay)'),
                  savepath,
                  savename = 'sep_agegroups_model3.Rds'))

summary(adults_only_ceph_model)


adults_by_loc <- adults_only_ceph_model %>%
  spread_draws(`b_interaction_mean_week_temperature_S:location_catcollecting_yard`, 
               `b_interaction_mean_week_temperature_S:location_catcubicles`,
               `b_interaction_mean_week_temperature_S:location_catshed_pen`) %>%
  select(-.draw, -.chain, -.iteration)

names(adults_by_loc) <- c('Temperature:collecting yard', 'Temperature:Cubicles', 'Temperature:ShedPen')

adults_by_loc %>%
  gather('predictor', 'coef') %>%
  ggplot() +
  stat_halfeye(aes(x = coef, y= predictor)) +
  geom_vline(xintercept = 0, linetype = 2) +
  xlab('Coefficient estimate') +
  ylab('Predictor')
  
  

h <- shed_pen_heifer_ceph_model %>%
  spread_draws(b_interaction_mean_week_temperature_S) %>%
  mutate(model = 'heifer (shed/pen)')

a <- collecting_yard_adult_ceph_model %>%
    spread_draws(b_interaction_mean_week_temperature_S) %>%
    mutate(model = 'asult(collecting yard)')

rbind(h, a) %>%
  ggplot() +
  stat_halfeye(aes(x = b_interaction_mean_week_temperature_S, y= model)) +
  geom_vline(xintercept = 0, linetype = 2) +
  xlab('Temperature (7 day mean)') +
  ylab('Model')


h <- shed_pen_heifer_ceph_model %>%
  spread_draws(b_interaction_mean_week_humidity_S) %>%
  mutate(model = 'heifer (shed/pen)')

a <- collecting_yard_adult_ceph_model %>%
    spread_draws(b_interaction_mean_week_humidity_S) %>%
    mutate(model = 'adult (collecting yard)')

rbind(h, a) %>%
  ggplot() +
  stat_halfeye(aes(x = b_interaction_mean_week_humidity_S, y= model)) 

rbind(h, a) %>%
  ggplot() +
  stat_halfeye(aes(x = b_interaction_mean_week_humidity_S, y= model)) +
  geom_vline(xintercept = 0, linetype = 2) +
  xlab('Humidity (7 day mean)') +
  ylab('Model')



summary(shed_pen_heifer_ceph_model)
summary(collecting_yard_adult_ceph_model)

collecting_yard_adult_ceph_model

new_data <- collecting_yard_adult_ceph_model$data %>%
  mutate(assay = NA, farm = NA, location_id = NA,
         mean_week_temperature_S = 0,
         mean_week_humidity_S = 0)
         
new_data
estimates <- as_tibble(inv_logit_scaled(fitted(collecting_yard_adult_ceph_model,
                    newdata = new_data,
                    re_formula = NA,
                    nlpar = 'interaction')))

assays <- as_tibble(inv_logit_scaled(fitted(collecting_yard_adult_ceph_model,
                    re_formula = NULL,
                    nlpar = 'interaction'))) %>%
  distinct()

names(assays) <- paste0('assay_', names(assays))

res <- cbind(estimates, collecting_yard_adult_ceph_model$data) %>%
  filter(am == 0)
assays <- cbind(assays, collecting_yard_adult_ceph_model$data) %>%
  filter(am == 0)
res
assays
final_res <- res %>%
  left_join(collecting_yard_adult_ceph, by = 'assay') %>%
  left_join(assays, by = 'assay') %>%
  distinct()

spline_plot <- final_res %>%
  ggplot() +
  geom_line(aes(x = date, y = Estimate)) +
  geom_ribbon(aes(x =  date, ymin = Q2.5, ymax = Q97.5), alpha = 0.3) +
  geom_point(aes(y = assay_Estimate, x = date), alpha = 0.1) +
  scale_y_continuous(trans = 'log10') +
  xlab('Date') +
  ylab('Estimated proportion resistant')

temp <- final_res %>%
  ggplot() +
  geom_line(aes(x = date, y = mean_week_temperature_S), colour = 'blue')

humid <- final_res %>%
  ggplot() +
  geom_line(aes(x = date, y = mean_week_humidity_S), colour = 'green')

gridExtra::grid.arrange(spline_plot, temp, humid, nrow = 3)

spline_plot

# Results table
```{r}
calc_effect_size <- function(model, am, location, predictor){
  if(predictor == 'temp'){
    res <- model  %>%
      spread_draws(b_interaction_mean_week_temperature_S) %>%
      mutate(model = as.factor(am),
             location = as.factor(location)) %>%
      select(-.chain, -.iteration, -.draw)
  }
  if(predictor == 'hum'){
    res <- model  %>%
      spread_draws(b_interaction_mean_week_humidity_S) %>%
      mutate(model = as.factor(am),
             location = as.factor(location)) %>%
      select(-.chain, -.iteration, -.draw)
  }
  return(res)
}

id <- 'B5'

amox_yard_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'yard_amox', '.Rds'))
amox_shed_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'shed_amox', '.Rds'))
ceph_yard_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'yard_ceph', '.Rds'))
ceph_shed_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'shed_ceph', '.Rds'))
cipro_yard_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'yard_cipro', '.Rds'))
cipro_shed_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'shed_cipro', '.Rds'))
strep_yard_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'yard_strep', '.Rds'))
strep_shed_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'shed_strep', '.Rds'))
tetra_yard_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'yard_tetra', '.Rds'))
tetra_shed_A1_temp <- readRDS(paste0(savepath, 'temp_only_A1_', 'shed_tetra', '.Rds'))

amox_yard_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'yard_amox', '.Rds'))
amox_shed_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'shed_amox', '.Rds'))
ceph_yard_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'yard_ceph', '.Rds'))
ceph_shed_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'shed_ceph', '.Rds'))
cipro_yard_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'yard_cipro', '.Rds'))
cipro_shed_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'shed_cipro', '.Rds'))
strep_yard_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'yard_strep', '.Rds'))
strep_shed_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'shed_strep', '.Rds'))
tetra_yard_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'yard_tetra', '.Rds'))
tetra_shed_A2_hum <- readRDS(paste0(savepath, 'hum_only_A2_', 'shed_tetra', '.Rds'))

 
all_ams_temp <- rbind(calc_effect_size(amox_yard_A1_temp, 'Amoxicillin', 'yard', 'temp'),
                          calc_effect_size(amox_shed_A1_temp, 'Amoxicillin', 'shed', 'temp'),
                          calc_effect_size(ceph_yard_A1_temp, 'Cephalexin', 'yard', 'temp'),
                          calc_effect_size(ceph_shed_A1_temp, 'Cephalexin', 'shed', 'temp'),
                          calc_effect_size(cipro_yard_A1_temp, 'Ciprofloxacin', 'yard', 'temp'),
                          calc_effect_size(cipro_shed_A1_temp, 'Ciprofloxacin', 'shed', 'temp'),
                          calc_effect_size(strep_yard_A1_temp, 'Streptomycin', 'yard', 'temp'),
                          calc_effect_size(strep_shed_A1_temp, 'Streptomycin', 'shed', 'temp'),
                         # calc_effect_size_LOC(tetra_yard_A1_temp, 'Tetracycline', 'yard', 'temp'),
                          calc_effect_size(tetra_shed_A1_temp, 'Tetracycline', 'shed', 'temp'))

levels(all_ams_temp$location) <- c('Adults in collecting yard', 'Heifers in sheds/pens')

all_ams_hum <- rbind(calc_effect_size(amox_yard_A2_hum, 'Amoxicillin', 'yard', 'hum'),
                          calc_effect_size(amox_shed_A2_hum, 'Amoxicillin', 'shed', 'hum'),
                          calc_effect_size(ceph_yard_A2_hum, 'Cephalexin', 'yard', 'hum'),
                          calc_effect_size(ceph_shed_A2_hum, 'Cephalexin', 'shed', 'hum'),
                          calc_effect_size(cipro_yard_A2_hum, 'Ciprofloxacin', 'yard', 'hum'),
                          calc_effect_size(cipro_shed_A2_hum, 'Ciprofloxacin', 'shed', 'hum'),
                          calc_effect_size(strep_yard_A2_hum, 'Streptomycin', 'yard', 'hum'),
                          calc_effect_size(strep_shed_A2_hum, 'Streptomycin', 'shed', 'hum'),
                         # calc_effect_size_LOC(tetra_yard_A2_hum, 'Tetracycline', 'yard', 'hum'),
                          calc_effect_size(tetra_shed_A2_hum, 'Tetracycline', 'shed', 'hum'))

levels(all_ams_hum$location) <- c('Adults in collecting yard', 'Heifers in sheds/pens')

median_and_CIs <- function(data){
  med <- as.character(round(median(data), 3))
  upp <- as.character(round(quantile(data, 0.975), 3))
  low <- as.character(round(quantile(data, 0.025), 3))
  sig <- ' '
  if((upp > 0 & low > 0) | (upp < 0 & low < 0) ){
    sig <- '*'
  }
  
  return(paste0(med, ' (', low, ', ', upp, ')  ', sig))
}

res_table_temp <- all_ams_temp %>%
  group_by(model, location) %>%
  summarise(temp_coef = median_and_CIs(b_interaction_mean_week_temperature_S))

res_table_hum <- all_ams_hum %>%
  group_by(model, location) %>%
  summarise(hum_coef = median_and_CIs(b_interaction_mean_week_humidity_S))

res_table <- res_table_temp %>%
  left_join(res_table_hum, by = c('model', 'location'))

write.csv(res_table, paste0(savepath, 'uni_var_results.csv'))

calc_effect_size(tetra_yard_A2_hum, 'Tetracycline', 'yard', 'hum') %>%
  group_by(model, location) %>%
  summarise(hum_coef = median_and_CIs(b_interaction_mean_week_humidity_S))
```

# Intercept only results
```{r}
amox_yard_A0_int <- readRDS(paste0(savepath, 'int_only_A0_', 'yard_amox', '.Rds'))
amox_yard_A0_int

new_data <- tibble(
    'mean_week_humidity_S' = rep(c(hum_1, hum_2), 2),
    'am' = c(rep(0, 2), rep(1, 2)),
    'assay' = NA,
    'log_dilution' = c(rep(log(0.1), 2), rep(0, 2)),
    'location_id' = NA,
    'farm' = NA)

get_assay_ests <- function(model, am, location){
  assay_res <- as.tibble(inv_logit_scaled(fitted(model,
         nlpar = 'interaction',
         re_formula = NULL,
         summary = T
         )))%>%
  distinct() %>%
  mutate(model = as.factor(am), 
         location = as.factor(location))
  
  return(assay_res)
}

yard_amox <- readRDS(paste0(savepath, 'int_only_A0_', 'yard_amox', '.Rds'))
shed_amox <- readRDS(paste0(savepath, 'int_only_A0_', 'shed_amox', '.Rds'))
yard_ceph <- readRDS(paste0(savepath, 'int_only_A0_', 'yard_ceph', '.Rds'))
shed_ceph <- readRDS(paste0(savepath, 'int_only_A0_', 'shed_ceph', '.Rds'))
yard_cipro <- readRDS(paste0(savepath, 'int_only_A0_', 'yard_cipro', '.Rds'))
shed_cipro <- readRDS(paste0(savepath, 'int_only_A0_', 'shed_cipro', '.Rds'))
yard_strep <- readRDS(paste0(savepath, 'int_only_A0_', 'yard_strep', '.Rds'))
shed_strep <- readRDS(paste0(savepath, 'int_only_A0_', 'shed_strep', '.Rds'))
yard_tetra <- readRDS(paste0(savepath, 'int_only_A0_', 'yard_tetra', '.Rds'))
shed_tetra <- readRDS(paste0(savepath, 'int_only_A0_', 'shed_tetra', '.Rds'))

all_assay_ests <- rbind(get_assay_ests(yard_amox, 'Amoxicillin', 'yard'),
                        get_assay_ests(shed_amox, 'Amoxicillin', 'shed'),
                        get_assay_ests(yard_ceph, 'Cephalexin', 'yard'),
                        get_assay_ests(shed_ceph, 'Cephalexin', 'shed'),
                        get_assay_ests(yard_cipro, 'Ciprofloxacin', 'yard'),
                        get_assay_ests(shed_cipro, 'Ciprofloxacin', 'shed'),
                        get_assay_ests(yard_strep, 'Streptomycin', 'yard'),
                        get_assay_ests(shed_strep, 'Streptomycin', 'shed'),
                        get_assay_ests(yard_tetra, 'Tetracycline', 'yard'),
                        get_assay_ests(shed_tetra, 'Tetracycline', 'shed'))
  

all_assay_ests
```


```{r, fig.width = 5, fig.height = 3}
all_assay_ests %>%
  ggplot() +
  stat_dist_eye(aes(y = Estimate, x = model, fill = location), alpha = 0.5, position = 'dodge') +
  scale_y_continuous(trans = 'log10') +
  scale_fill_manual(values = c(dual_greens[2], dual_blues[2])) +
  theme_minimal() +
  ylab('Estimated proportion resistant') +
  xlab('Antimicrobial')

summary_tab <- all_assay_ests %>%
  group_by(model, location) %>%
  summarise(median(Estimate),
            quantile(Estimate, 0.25),
            quantile(Estimate, 0.75))

write.csv(summary_tab, paste0(savepath, 'summary_tab_median_res.csv'))

```

